### 2023-05-23 docs/response-time-research.md
Update research

# Accelerating response times for high-traffic social media platforms

By Kostadinov, Stoyan S.L.

<!-- TOC -->
* [Accelerating response times for high-traffic social media platforms](#accelerating-response-times-for-high-traffic-social-media-platforms)
  * [Introduction](#introduction)
    * [Context](#context)
    * [Research questions and objectives](#research-questions-and-objectives)
    * [Methodology](#methodology)
    * [Constraints](#constraints)
    * [Glossary](#glossary)
  * [Literature review](#literature-review)
  * [Non-functional testing](#non-functional-testing)
  * [References](#references)
<!-- TOC -->

## Introduction

### Context

The majority of content on Reddit consists of text-based and media-based (videos and images) posts.
According to recent statistics, Reddit received an average of 30 billion monthly views in 2020,
making it the 6th largest social media platform in terms of
traffic.[[x]](https://www.businessofapps.com/data/reddit-statistics/)[[x]](https://www.similarweb.com/top-websites/computers-electronics-and-technology/social-networks-and-online-communities/)
As Reddit's revenue model heavily relies on
advertising[[x]](https://www.businessofapps.com/data/reddit-statistics/), the company stands to earn
more money with increased user visits to the platform.

Website speed is widely recognized as a crucial factor in user experience, with even a 1-second
delay in page load time leading to a 7% decrease in
conversions.[[x]](https://www.truconversion.com/traffic/decrease-page-load-time/)[[x]](https://cxl.com/blog/11-low-hanging-fruits-for-increasing-website-speed-and-conversions/)
When considering Reddit's annual revenue of $350
million[[x]](https://www.businessofapps.com/data/reddit-statistics/), this conversion loss
translates to a potential revenue loss of $24.5 million per year.

These factors clearly indicate that Reddit and other social media platforms have a strong incentive
to optimize their response times.

### Research questions and objectives

The goal of this research paper is to gain insight into different optimization techniques and
provide recommendations for the _not-reddit_[[x]](https://github.com/stoyanK7/not-reddit/) social
media platform.

> _not-reddit_ is a social news aggregation platform with sub-communities, messaging, and awards
> that allows users to post and share content, vote on submissions, and comment on posts.

---

> _**How can response times for the not-reddit social media platform be accelerated?**_

In order go get a better understanding of the problem, the following sub-questions will be
addressed:

> - _How does a request at not-reddit currently look like?_
> - _How does a request at not-reddit currently perform?_
> - _What performance-improving techniques do major social media platforms use?_
> - _How can the impact different techniques' be measured and evaluated?_

### Methodology

To achieve the research objectives and address the research questions, the following methodology
will be employed:

1. **Literature study** - A literature review will be conducted to gain insight into the
   performance-improving techniques used by major social media platforms.
2. **Non-functional testing** - A series of non-functional tests will be conducted to measure the
   performance of the not-reddit platform before and after applying the performance-improving
   techniques.
3. **IT architecture sketching** - A sketch of the not-reddit IT architecture will be created to
   identify the components that can be optimized.

> Note: The above methods are taken from ICT Research
> methods.[[x]](https://ictresearchmethods.nl/Methods)

### Constraints

The research is constrained by the following factors:

- **Time**\
  The research is limited to 3 weeks.
- **Resources**\
  The research is limited to the resources available to the author. All tests are ran from
  a `ASUSTeK COMPUTER INC. ZenBook UX434FLC_UX434FL` laptop with `8GB` of RAM and
  an `Intel(R) Core(TM) i7-10510U CPU @ 1.80GHz` processor.
- **Scope**\
  The research is limited to the not-reddit platform and does not consider other social media
  platforms.
- **Data**\
  The research is limited to the data available to the author. The not-reddit platform is a
  prototype and does not have any real users. The data used for the research is generated by
  the author.
- **Expertise**\
  The research is limited to the author's expertise. The author is a student with limited
  experience in the field of performance optimization.

### Glossary

| Term | Definition |
|------|------------|
| xxx  |            |

## Baseline

![img](img/2023-05-22-architecture-container.png)

## Literature review

## Non-functional testing

## References

TODO

### 2023-05-23 docs/response-time-research.md
Add diagram for post service request route

@@
 <!-- TOC -->
+
 * [Accelerating response times for high-traffic social media platforms](#accelerating-response-times-for-high-traffic-social-media-platforms)
@@
     * [References](#references)
+
 <!-- TOC -->
@@
 
-![img](img/2023-05-22-architecture-container.png)
+On a system level, the not-reddit platform consists of 4 components - not-reddit system itself,
+Azure Active Directory (AAD), Azure Blob Storage (ABS), and Azure Email Communication Service (
+AECS).
+![img](img/2023-05-22-architecture-system.png)
+
+The scope of this research is focuses on the post service which is responsible for handling creation
+and retrieval of posts and media. A typical request starts from the client (browser), goes
+through the API gateway and lands in the Post API. The API will retrieve the post from the database
+and send it back to the client. Depending of the `type` of the post, the client will send additional
+request for the media. In total, for a media post, 2 requests will be made.
+![img](img/2023-05-23-architecture-post.png)
 

### 2023-05-23 docs/response-time-research.md
Update research

@@
         * [Glossary](#glossary)
+    * [Baseline](#baseline)
+        * [Baseline results](#baseline-results)
     * [Literature review](#literature-review)
@@
   a `ASUSTeK COMPUTER INC. ZenBook UX434FLC_UX434FL` laptop with `8GB` of RAM and
-  an `Intel(R) Core(TM) i7-10510U CPU @ 1.80GHz` processor.
+  an `Intel(R) Core(TM) i7-10510U CPU @ 1.80GHz` processor. The Azure Kubernetes Services cluster is
+  running on a `Standard_B4ms` machine with 1 node pool.
 - **Scope**\
@@
 
+The landing page will contain 6 text and 4 media posts.
+
 ### Glossary
+TODO: look for terms at the end of the document and add them here
 
 | Term                            | Definition                                                                                                                                                                 |
-|------|------------|
-| xxx  |            |
+|---------------------------------|----------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
+| Azure Kubernetes Services (AKS) | A fully managed container orchestration service provided by Microsoft Azure, enabling developers to deploy, scale, and manage containerized applications using Kubernetes.
+|
+
+## Measurements
+
+The following measurements will be used to evaluate the performance of the not-reddit platform:
+
+- **Latency**\
+  The time it takes for a request to be sent from the client to the server and back.
+- **Throughput**\
+  The number of requests that can be processed per second.
+- **Error rate**\
+  The percentage of requests that fail.
+- **CPU usage**\
+  The percentage of CPU used by the application.
+- **Network usage**\
+  The percentage of network bandwidth used by the application.
+
+Latency, Throughput and Error rate are measured using _Apache
+JMeter_[[x]](https://jmeter.apache.org/) and _Azure Kubernetes
+Metrics_.[[x]](https://learn.microsoft.com/en-us/azure/aks/monitor-aks)
 
@@
 ![img](img/2023-05-22-architecture-system.png)
+<p align="center"><i>Figure 1: System architecture</i></p>
 
@@
 ![img](img/2023-05-23-architecture-post.png)
+<p align="center"><i>Figure 2: Post service architecture</i></p>
+
+### Baseline results
 

### 2023-05-24 api/src/main/user/crud.py
Add endpoint for deleting a user

@@ -22,3 +22,8 @@ def get_user_by_email(db: Session, email: str) -> UserModel:
 def get_user_by_username_or_email(db: Session, username: str, email: str) -> UserModel:
     return db.query(UserModel)\
         .filter((UserModel.username == username) or (UserModel.email == email)).first()
+
+
+def delete_user(db: Session, email: str):
+    db.query(UserModel).filter(UserModel.email == email).delete()
+    db.commit()

### 2023-05-24 api/src/main/user/router.py

@@ -1,5 +1,5 @@
 from fastapi import APIRouter, Depends, Request, BackgroundTasks
-from starlette.status import HTTP_201_CREATED, HTTP_200_OK
+from starlette.status import HTTP_201_CREATED, HTTP_200_OK, HTTP_204_NO_CONTENT
 from sqlalchemy.orm import Session
 
 from src.main.shared.database.main import get_db
@@ -49,5 +49,16 @@ async def create_user(request: Request, background_tasks: BackgroundTasks,
     oid = get_access_token_oid(request)
     background_tasks.add_task(emit_user_registration_event, request=request, email=email, oid=oid,
                               username=new_username)
+
+    return
+
+
+@router.delete("", status_code=HTTP_204_NO_CONTENT)
+def delete_user(request: Request, db: Session = Depends(get_db)):
+    email = get_access_token_preferred_username(request)
+    user = crud.get_user_by_email(db=db, email=email)
+    assert_is_user_exists(user)
+
+    crud.delete_user(db=db, email=email)
 
     return

### 2023-05-24 api/src/test/user/test_user.py

@@ -1,4 +1,5 @@
-from starlette.status import HTTP_200_OK, HTTP_201_CREATED, HTTP_404_NOT_FOUND, HTTP_409_CONFLICT
+from starlette.status import HTTP_200_OK, HTTP_201_CREATED, HTTP_404_NOT_FOUND, HTTP_409_CONFLICT, \
+    HTTP_204_NO_CONTENT
 import jwt
 
 from src.main.user.model import User as UserModel
@@ -71,10 +72,10 @@ def test_get_username_with_non_existing_user(client, session, mock_user_with_use
 def test_check_if_registered(client, session, mock_user_with_username):
     """Assert that user is registered."""
     user = mock_user_with_username
-    jwt_token = jwt.encode({"preferred_username": user["email"]}, "secret", algorithm="HS256")
     session.add(UserModel(**user))
     session.commit()
 
+    jwt_token = jwt.encode({"preferred_username": user["email"]}, "secret", algorithm="HS256")
     response = client.get("/api/user/registered",
                           headers={"Authorization": f"Bearer {jwt_token}"})
 
@@ -92,3 +93,27 @@ def test_check_if_registered_not_registered(client, session, mock_user):
 
     assert response.status_code == HTTP_200_OK
     assert response.json() == {"registered": False}
+
+
+def test_delete_user(client, session, mock_user_with_username):
+    """Assert that deleting a user works."""
+    user = mock_user_with_username
+    session.add(UserModel(**user))
+    session.commit()
+
+    jwt_token = jwt.encode({"preferred_username": user["email"]}, "secret", algorithm="HS256")
+    response = client.delete("/api/user",
+                             headers={"Authorization": f"Bearer {jwt_token}"})
+
+    assert response.status_code == HTTP_204_NO_CONTENT
+    assert session.query(UserModel).filter_by(email=user["email"]).first() is None
+
+
+def test_delete_user_non_existing_user(client, session):
+
+    jwt_token = jwt.encode({"preferred_username": "nonexistingemail"}, "secret", algorithm="HS256")
+    response = client.delete("/api/user",
+                             headers={"Authorization": f"Bearer {jwt_token}"})
+
+    assert response.status_code == HTTP_404_NOT_FOUND
+    assert response.json() == {"detail": "User not found"}

### 2023-05-24 api/src/main/shared/amqp/amqp_consumer.py
Make queues non-exclusive so multiple services can connect to one

@@ -31,7 +31,7 @@ class AmqpConsumer:
         exchange = await channel.declare_exchange(self.exchange_name, exchange_type)
         logger.info(f"Declared exchange '{self.exchange_name}' of type {exchange_type}.")
 
-        queue = await channel.declare_queue(exclusive=True, name=self.queue_name)
+        queue = await channel.declare_queue(exclusive=False, name=self.queue_name)
         logger.info(f"Declared queue '{self.queue_name}'.")
 
         await queue.bind(exchange)

### 2023-05-24 api/src/main/shared/amqp/settings.py
Implement user_deleted event

@@ -17,3 +17,4 @@ class AmqpSettings(BaseSettings):
     AMQP_COMMENT_CREATED_EXCHANGE_NAME: str = get_env("AMQP_COMMENT_CREATED_EXCHANGE_NAME")
     AMQP_POST_VOTE_CASTED_EXCHANGE_NAME: str = get_env("AMQP_POST_VOTE_CASTED_EXCHANGE_NAME")
     AMQP_COMMENT_VOTE_CASTED_EXCHANGE_NAME: str = get_env("AMQP_COMMENT_VOTE_CASTED_EXCHANGE_NAME")
+    AMQP_USER_DELETED_EXCHANGE_NAME: str = get_env("AMQP_USER_DELETED_EXCHANGE_NAME")

### 2023-05-24 api/src/main/user/lifespan.py

@@ -14,6 +14,8 @@ async def lifespan(app: UserService) -> Lifespan[AppType]:
     loop = asyncio.get_running_loop()
     task = loop.create_task(app.user_registered_amqp_publisher.prepare_connection(loop))
     await task
+    task = loop.create_task(app.user_deleted_amqp_publisher.prepare_connection(loop))
+    await task
     yield
 
 

### 2023-05-24 api/src/main/user/router.py

@@ -6,7 +6,7 @@ from src.main.shared.database.main import get_db
 from src.main.shared.jwt_util import get_access_token_preferred_username, get_access_token_oid
 from src.main.user.settings import settings
 from src.main.user.util import assert_is_username_and_email_not_taken, assert_is_user_exists, \
-    emit_user_registration_event
+    emit_user_registered_event, emit_user_deleted_event
 from random_username.generate import generate_username
 from src.main.user import crud
 
@@ -47,18 +47,21 @@ async def create_user(request: Request, background_tasks: BackgroundTasks,
     crud.create_user(db=db, username=new_username, email=email)
 
     oid = get_access_token_oid(request)
-    background_tasks.add_task(emit_user_registration_event, request=request, email=email, oid=oid,
+    background_tasks.add_task(emit_user_registered_event, request=request, email=email, oid=oid,
                               username=new_username)
 
     return
 
 
 @router.delete("", status_code=HTTP_204_NO_CONTENT)
-def delete_user(request: Request, db: Session = Depends(get_db)):
+def delete_user(request: Request, background_tasks: BackgroundTasks, db: Session = Depends(get_db)):
     email = get_access_token_preferred_username(request)
     user = crud.get_user_by_email(db=db, email=email)
     assert_is_user_exists(user)
 
     crud.delete_user(db=db, email=email)
+
+    oid = get_access_token_oid(request)
+    background_tasks.add_task(emit_user_deleted_event, request=request, oid=oid)
 
     return

### 2023-05-24 api/src/main/user/service.py

@@ -9,10 +9,15 @@ class UserService(FastAPI):
         super().__init__(*args, **kwargs)
 
         self.user_registered_amqp_publisher = None
+        self.user_deleted_amqp_publisher = None
         self.initialize_amqp_publishers()
 
     def initialize_amqp_publishers(self):
         self.user_registered_amqp_publisher = AmqpPublisher(
             settings.AMQP_URL,
             exchange_name=settings.AMQP_USER_REGISTERED_EXCHANGE_NAME,
+        )
+        self.user_deleted_amqp_publisher = AmqpPublisher(
+            settings.AMQP_URL,
+            exchange_name=settings.AMQP_USER_DELETED_EXCHANGE_NAME,
         )

### 2023-05-24 api/src/main/user/util.py

@@ -25,7 +25,7 @@ def assert_is_user_exists(user):
         )
 
 
-async def emit_user_registration_event(request: Request, email: str, oid: str, username: str):
+async def emit_user_registered_event(request: Request, email: str, oid: str, username: str):
     body = json.dumps({
         "recipients": [email],
         "content_topic": "user_registration",
@@ -33,3 +33,10 @@ async def emit_user_registration_event(request: Request, email: str, oid: str, u
         "username": username
     })
     await request.app.user_registered_amqp_publisher.send_message(str(body))
+
+
+async def emit_user_deleted_event(request: Request, oid: str):
+    body = json.dumps({
+        "oid": oid
+    })
+    await request.app.user_deleted_amqp_publisher.send_message(str(body))

### 2023-05-24 api/src/main/post/crud.py
Delete all user posts upon user deletion

@@ -64,12 +64,24 @@ def delete_post_by_id(db: Session, post_id: int):
     return
 
 
+def delete_user_posts(db: Session, username: str):
+    db.query(PostModel).filter(PostModel.username == username).delete()
+    db.commit()
+    return
+
+
 def insert_user(db: Session, username: str, oid: str):
     db_user = UserModel(username=username, oid=oid)
     db.add(db_user)
     db.commit()
     db.refresh(db_user)
     return db_user
+
+
+def delete_user(db: Session, oid: str):
+    db.query(UserModel).filter(UserModel.oid == oid).delete()
+    db.commit()
+    return
 
 
 def get_username_by_oid(db: Session, oid: str):

### 2023-05-24 api/src/main/post/lifespan.py

@@ -19,6 +19,8 @@ async def lifespan(app: PostService) -> Lifespan[AppType]:
     await task
     task = loop.create_task(app.post_vote_casted_amqp_consumer.consume(loop))
     await task
+    task = loop.create_task(app.user_deleted_amqp_consumer.consume(loop))
+    await task
     yield
 
 

### 2023-05-24 api/src/main/post/service.py

@@ -3,7 +3,7 @@ from fastapi import FastAPI
 from src.main.shared.amqp.amqp_consumer import AmqpConsumer
 from src.main.shared.amqp.amqp_publisher import AmqpPublisher
 from src.main.post.settings import settings
-from src.main.post.util import handle_user_registration, handle_vote_casted
+from src.main.post.util import handle_user_registration, handle_vote_casted, handle_user_deleted
 
 
 class PostService(FastAPI):
@@ -12,6 +12,7 @@ class PostService(FastAPI):
 
         self.user_registered_amqp_consumer = None
         self.post_vote_casted_amqp_consumer = None
+        self.user_deleted_amqp_consumer = None
         self.initialize_amqp_consumers()
 
         self.post_created_amqp_publisher = None
@@ -29,6 +30,12 @@ class PostService(FastAPI):
             exchange_name=settings.AMQP_POST_VOTE_CASTED_EXCHANGE_NAME,
             queue_name=settings.AMQP_POST_VOTE_CASTED_QUEUE_NAME,
             incoming_message_handler=handle_vote_casted,
+        )
+        self.user_deleted_amqp_consumer = AmqpConsumer(
+            settings.AMQP_URL,
+            exchange_name=settings.AMQP_USER_DELETED_EXCHANGE_NAME,
+            queue_name=settings.AMQP_USER_DELETED_QUEUE_NAME,
+            incoming_message_handler=handle_user_deleted,
         )
 
     def initialize_amqp_publishers(self):

### 2023-05-24 api/src/main/post/settings.py

@@ -7,6 +7,7 @@ class PostServiceSettings(AmqpSettings):
     # AMQP
     AMQP_USER_REGISTERED_QUEUE_NAME: str = "post_service_user_registered_queue"
     AMQP_POST_VOTE_CASTED_QUEUE_NAME: str = "post_service_post_vote_casted_queue"
+    AMQP_USER_DELETED_QUEUE_NAME: str = "post_service_post_user_deleted_queue"
     # Azure Blob Storage
     BLOB_STORAGE_ACCOUNT_NAME: str = get_env("BLOB_STORAGE_ACCOUNT_NAME")
     BLOB_STORAGE_CONNECTION_STRING: str = get_env("BLOB_STORAGE_CONNECTION_STRING")

### 2023-05-24 api/src/main/post/util.py

@@ -135,3 +135,11 @@ def handle_vote_casted(message: AbstractIncomingMessage) -> None:
         crud.cast_upvote(db=db, post_id=body["post_id"])
     elif body["vote_type"] == "down":
         crud.cast_downvote(db=db, post_id=body["post_id"])
+
+
+def handle_user_deleted(message: AbstractIncomingMessage) -> None:
+    body = decode_body_and_convert_to_dict(message.body)
+    db = next(get_db())
+    crud.delete_user(db=db, oid=body["oid"])
+    username = crud.get_username_by_oid(db=db, oid=body["oid"])
+    crud.delete_user_posts(db=db, username=username)

### 2023-05-24 api/src/main/comment/crud.py
Delete user comments upon user deletion

@@ -37,6 +37,12 @@ def create_comment(db: Session, comment: dict):
     return db_comment
 
 
+def delete_user_comments(db: Session, username: str):
+    db.query(CommentModel).filter(CommentModel.username == username).delete()
+    db.commit()
+    return
+
+
 def cast_upvote(db: Session, comment_id: int):
     db_post = db.query(CommentModel).filter(CommentModel.id == comment_id).first()
     db_post.votes += 1
@@ -63,6 +69,12 @@ def insert_user(db: Session, username: str, oid: str):
     db.commit()
     db.refresh(db_user)
     return db_user
+
+
+def delete_user(db: Session, oid: str):
+    db.query(UserModel).filter(UserModel.oid == oid).delete()
+    db.commit()
+    return
 
 
 def get_username_by_oid(db: Session, oid: str):

### 2023-05-24 api/src/main/comment/lifespan.py

@@ -19,6 +19,8 @@ async def lifespan(app: CommentService) -> Lifespan[AppType]:
     await task
     task = loop.create_task(app.comment_vote_casted_amqp_consumer.consume(loop))
     await task
+    task = loop.create_task(app.user_deleted_amqp_consumer.consume(loop))
+    await task
     yield
 
 

### 2023-05-24 api/src/main/comment/service.py

@@ -2,7 +2,8 @@ from fastapi import FastAPI
 
 from src.main.shared.amqp.amqp_consumer import AmqpConsumer
 from src.main.comment.settings import settings
-from src.main.comment.util import handle_user_registration, handle_post_creation, handle_vote_casted
+from src.main.comment.util import handle_user_registration, handle_post_creation, \
+    handle_vote_casted, handle_user_deleted
 from src.main.shared.amqp.amqp_publisher import AmqpPublisher
 
 
@@ -13,6 +14,7 @@ class CommentService(FastAPI):
         self.user_registered_amqp_consumer = None
         self.post_created_amqp_consumer = None
         self.comment_vote_casted_amqp_consumer = None
+        self.user_deleted_amqp_consumer = None
         self.initialize_amqp_consumers()
 
         self.comment_created_amqp_publisher = None
@@ -36,6 +38,12 @@ class CommentService(FastAPI):
             exchange_name=settings.AMQP_COMMENT_VOTE_CASTED_EXCHANGE_NAME,
             queue_name=settings.AMQP_COMMENT_VOTE_CASTED_QUEUE_NAME,
             incoming_message_handler=handle_vote_casted,
+        )
+        self.user_deleted_amqp_consumer = AmqpConsumer(
+            settings.AMQP_URL,
+            exchange_name=settings.AMQP_USER_DELETED_EXCHANGE_NAME,
+            queue_name=settings.AMQP_USER_DELETED_QUEUE_NAME,
+            incoming_message_handler=handle_user_deleted,
         )
 
     def initialize_amqp_publishers(self):

### 2023-05-24 api/src/main/comment/settings.py

@@ -6,6 +6,7 @@ class CommentServiceSettings(AmqpSettings):
     AMQP_USER_REGISTERED_QUEUE_NAME: str = "comment_service_user_registered_queue"
     AMQP_POST_CREATED_QUEUE_NAME: str = "comment_service_post_created_queue"
     AMQP_COMMENT_VOTE_CASTED_QUEUE_NAME: str = "comment_service_comment_vote_casted_queue"
+    AMQP_USER_DELETED_QUEUE_NAME: str = "comment_service_user_deleted_queue"
 
 
 settings = CommentServiceSettings()

### 2023-05-24 api/src/main/comment/util.py

@@ -39,6 +39,14 @@ def handle_vote_casted(message: AbstractIncomingMessage):
         crud.cast_downvote(db=db, comment_id=body["comment_id"])
 
 
+def handle_user_deleted(message: AbstractIncomingMessage):
+    body = decode_body_and_convert_to_dict(message.body)
+    db = next(get_db())
+    crud.delete_user(db=db, oid=body["oid"])
+    username = crud.get_username_by_oid(db=db, oid=body["oid"])
+    crud.delete_user_comments(db=db, username=username)
+
+
 def assert_post_exists(db: Session, post_id: int):
     post_exists = crud.get_post_by_id(db=db, post_id=post_id)
     if not post_exists:

### 2023-05-24 api/src/main/vote/crud.py
Delete user votes on user deletion

@@ -18,12 +18,24 @@ def cast_vote(db: Session, vote: dict):
     return
 
 
+def delete_user_votes(db: Session, username: str):
+    db.query(VoteModel).filter(VoteModel.username == username).delete()
+    db.commit()
+    return
+
+
 def insert_user(db: Session, username: str, oid: str):
     db_user = UserModel(username=username, oid=oid)
     db.add(db_user)
     db.commit()
     db.refresh(db_user)
     return db_user
+
+
+def delete_user(db: Session, oid: str):
+    db.query(UserModel).filter(UserModel.oid == oid).delete()
+    db.commit()
+    return
 
 
 def insert_post(db: Session, post: dict):

### 2023-05-24 api/src/main/vote/lifespan.py

@@ -23,6 +23,8 @@ async def lifespan(app: VoteService) -> Lifespan[AppType]:
     await task
     task = loop.create_task(app.comment_vote_casted_amqp_publisher.prepare_connection(loop))
     await task
+    task = loop.create_task(app.user_deleted_amqp_consumer.consume(loop))
+    await task
     yield
 
 

### 2023-05-24 api/src/main/vote/service.py

@@ -4,7 +4,7 @@ from src.main.shared.amqp.amqp_consumer import AmqpConsumer
 from src.main.shared.amqp.amqp_publisher import AmqpPublisher
 from src.main.vote.settings import settings
 from src.main.vote.util import handle_user_registration, handle_post_creation, \
-    handle_comment_creation
+    handle_comment_creation, handle_user_deleted
 
 
 class VoteService(FastAPI):
@@ -14,6 +14,7 @@ class VoteService(FastAPI):
         self.user_registered_amqp_consumer = None
         self.post_created_amqp_consumer = None
         self.comment_created_amqp_consumer = None
+        self.user_deleted_amqp_consumer = None
         self.initialize_amqp_consumers()
 
         self.post_vote_casted_amqp_publisher = None
@@ -38,6 +39,12 @@ class VoteService(FastAPI):
             exchange_name=settings.AMQP_COMMENT_CREATED_EXCHANGE_NAME,
             queue_name=settings.AMQP_COMMENT_CREATED_QUEUE_NAME,
             incoming_message_handler=handle_comment_creation
+        )
+        self.user_deleted_amqp_consumer = AmqpConsumer(
+            settings.AMQP_URL,
+            exchange_name=settings.AMQP_USER_DELETED_EXCHANGE_NAME,
+            queue_name=settings.AMQP_USER_DELETED_QUEUE_NAME,
+            incoming_message_handler=handle_user_deleted
         )
 
     def initialize_amqp_publishers(self):

### 2023-05-24 api/src/main/vote/settings.py

@@ -6,6 +6,7 @@ class VoteServiceSettings(AmqpSettings):
     AMQP_USER_REGISTERED_QUEUE_NAME: str = "vote_service_user_registered_queue"
     AMQP_POST_CREATED_QUEUE_NAME: str = "vote_service_post_created_queue"
     AMQP_COMMENT_CREATED_QUEUE_NAME: str = "vote_service_comment_created_queue"
+    AMQP_USER_DELETED_QUEUE_NAME: str = "vote_service_user_deleted_queue"
 
 
 settings = VoteServiceSettings()

### 2023-05-24 api/src/main/vote/util.py

@@ -33,6 +33,14 @@ def handle_user_registration(message: AbstractIncomingMessage):
     crud.insert_user(db=db, username=username, oid=oid)
 
 
+def handle_user_deleted(message: AbstractIncomingMessage):
+    body = decode_body_and_convert_to_dict(message.body)
+    db = next(get_db())
+    crud.delete_user(db=db, oid=body['oid'])
+    username = crud.get_username_by_oid(db=db, oid=body['oid'])
+    crud.delete_user_votes(db=db, username=username)
+
+
 def handle_post_creation(message: AbstractIncomingMessage):
     body = decode_body_and_convert_to_dict(message.body)
     db = next(get_db())

### 2023-05-24 api/src/main/comment/util.py
Fix wrong order of statements during user deletion

@@ -42,8 +42,8 @@ def handle_vote_casted(message: AbstractIncomingMessage):
 def handle_user_deleted(message: AbstractIncomingMessage):
     body = decode_body_and_convert_to_dict(message.body)
     db = next(get_db())
-    crud.delete_user(db=db, oid=body["oid"])
     username = crud.get_username_by_oid(db=db, oid=body["oid"])
+    crud.delete_user(db=db, oid=body["oid"])
     crud.delete_user_comments(db=db, username=username)
 
 

### 2023-05-24 api/src/main/post/settings.py

@@ -7,7 +7,7 @@ class PostServiceSettings(AmqpSettings):
     # AMQP
     AMQP_USER_REGISTERED_QUEUE_NAME: str = "post_service_user_registered_queue"
     AMQP_POST_VOTE_CASTED_QUEUE_NAME: str = "post_service_post_vote_casted_queue"
-    AMQP_USER_DELETED_QUEUE_NAME: str = "post_service_post_user_deleted_queue"
+    AMQP_USER_DELETED_QUEUE_NAME: str = "post_service_user_deleted_queue"
     # Azure Blob Storage
     BLOB_STORAGE_ACCOUNT_NAME: str = get_env("BLOB_STORAGE_ACCOUNT_NAME")
     BLOB_STORAGE_CONNECTION_STRING: str = get_env("BLOB_STORAGE_CONNECTION_STRING")

### 2023-05-24 api/src/main/post/util.py

@@ -140,6 +140,6 @@ def handle_vote_casted(message: AbstractIncomingMessage) -> None:
 def handle_user_deleted(message: AbstractIncomingMessage) -> None:
     body = decode_body_and_convert_to_dict(message.body)
     db = next(get_db())
-    crud.delete_user(db=db, oid=body["oid"])
     username = crud.get_username_by_oid(db=db, oid=body["oid"])
+    crud.delete_user(db=db, oid=body["oid"])
     crud.delete_user_posts(db=db, username=username)

### 2023-05-24 api/src/main/vote/util.py

@@ -36,8 +36,8 @@ def handle_user_registration(message: AbstractIncomingMessage):
 def handle_user_deleted(message: AbstractIncomingMessage):
     body = decode_body_and_convert_to_dict(message.body)
     db = next(get_db())
-    crud.delete_user(db=db, oid=body['oid'])
     username = crud.get_username_by_oid(db=db, oid=body['oid'])
+    crud.delete_user(db=db, oid=body['oid'])
     crud.delete_user_votes(db=db, username=username)
 
 

### 2023-05-24 docs/response-time-research.md
Move measurements section in constraints

@@
 
-### Glossary
-TODO: look for terms at the end of the document and add them here
-
-| Term                            | Definition                                                                                                                                                                 |
-|---------------------------------|----------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
-| Azure Kubernetes Services (AKS) | A fully managed container orchestration service provided by Microsoft Azure, enabling developers to deploy, scale, and manage containerized applications using Kubernetes.
-|
-
-## Measurements
+#### Measurements
 
@@
   The percentage of requests that fail.
-- **CPU usage**\
-  The percentage of CPU used by the application.
-- **Network usage**\
-  The percentage of network bandwidth used by the application.
 
-Latency, Throughput and Error rate are measured using _Apache
-JMeter_[[x]](https://jmeter.apache.org/) and _Azure Kubernetes
-Metrics_.[[x]](https://learn.microsoft.com/en-us/azure/aks/monitor-aks)
+All are measured using _Apache JMeter_.[[x]](https://jmeter.apache.org/) A total of 5 requests
+different requests will be made to simulate real user behavior:
+
+- /api/post?sort_by=hot&page=0
+- /api/post/media/7.png
+- /api/post/media/8.png
+- /api/post/media/9.png
+- /api/post/media/10.png
+
+The number of threads will be set to 1000 and the ramp-up period to 1 second.
+
+### Glossary
+
+TODO: look for terms at the end of the document and add them here
+
+| Term                            | Definition                                                                                                                                                                 |
+|---------------------------------|----------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
+| Azure Kubernetes Services (AKS) | A fully managed container orchestration service provided by Microsoft Azure, enabling developers to deploy, scale, and manage containerized applications using Kubernetes.
+|
 

### 2023-05-25 api/src/main/award/main.py
Add award service

@@ -1,0 +1,15 @@
+from starlette.middleware.cors import CORSMiddleware
+
+from src.main.award.router import router
+from src.main.shared.cors.settings import settings as cors_settings
+from src.main.award.service import AwardService
+
+app = AwardService()
+app.include_router(router)
+app.add_middleware(
+    CORSMiddleware,
+    allow_origins=cors_settings.CORS_ALLOWED_ORIGINS,
+    allow_credentials=True,
+    allow_methods=['*'],
+    allow_headers=['*']
+)

### 2023-05-25 api/src/main/award/router.py

@@ -1,0 +1,67 @@
+import stripe
+
+from fastapi import APIRouter, Request
+from stripe.error import SignatureVerificationError
+from starlette.responses import RedirectResponse
+
+from src.main.award.settings import settings
+
+router = APIRouter(prefix=settings.SERVICE_PREFIX)
+
+stripe.api_key = settings.STRIPE_API_KEY
+
+
+@router.post("/stripe_webhooks")
+def webhook(request: Request, body: dict):
+    event = None
+    payload = body
+
+    if settings.EDNPOINT_SECRET:
+        # Only verify the event if there is an endpoint secret defined
+        # Otherwise use the basic event deserialized with json
+        sig_header = request.headers['stripe-signature']
+        try:
+            event = stripe.Webhook.construct_event(
+                payload, sig_header, settings.EDNPOINT_SECRET
+            )
+        except stripe.error.SignatureVerificationError as e:
+            print('⚠️  Webhook signature verification failed.' + str(e))
+            return {"success": False}
+
+        # Handle the event
+    if event and event['type'] == 'payment_intent.succeeded':
+        payment_intent = event['data']['object']  # contains a stripe.PaymentIntent
+        print('Payment for {} succeeded'.format(payment_intent['amount']))
+        # Then define and call a method to handle the successful payment intent.
+        # handle_payment_intent_succeeded(payment_intent)
+    elif event['type'] == 'payment_method.attached':
+        payment_method = event['data']['object']  # contains a stripe.PaymentMethod
+        # Then define and call a method to handle the successful attachment of a PaymentMethod.
+        # handle_payment_method_attached(payment_method)
+    else:
+        # Unexpected event type
+        print('Unhandled event type {}'.format(event['type']))
+
+    # Handle the event
+    print('Handled event type {}'.format(event['type']))
+
+    return {"success": True}
+
+
+@router.post("/session")
+def create_checkout_session():
+    try:
+        checkout_session = stripe.checkout.Session.create(
+            line_items=[
+                {
+                    'price': 'price_1NBcsqHMj8LggMg2UidsD64r',
+                    'quantity': 1,
+                },
+            ],
+            mode='payment',
+            success_url=settings.UI_URL + '/award?success=true',
+            cancel_url=settings.UI_URL + '/award?canceled=true',
+        )
+        return RedirectResponse(url=checkout_session.url, status_code=303)
+    except Exception as e:
+        return str(e)

### 2023-05-25 api/src/main/award/service.py

@@ -1,0 +1,6 @@
+from fastapi import FastAPI
+
+
+class AwardService(FastAPI):
+    def __init__(self, *args, **kwargs):
+        super().__init__(*args, **kwargs)

### 2023-05-25 api/src/main/award/settings.py

@@ -1,0 +1,13 @@
+from src.main.shared.env import get_env
+
+
+class AwardServiceSettings:
+    SERVICE_PREFIX: str = "/api/award"
+    STRIPE_API_KEY = get_env("STRIPE_API_KEY")
+    STRIPE_SILVER_AWARD_PRICE = get_env("STRIPE_SILVER_AWARD_PRICE")
+    STRIPE_GOLD_AWARD_PRICE = get_env("STRIPE_GOLD_AWARD_PRICE")
+    STRIPE_PLATINUM_AWARD_PRICE = get_env("STRIPE_PLATINUM_AWARD_PRICE")
+    UI_URL = get_env("UI_URL")
+
+
+settings = AwardServiceSettings()

### 2023-05-25 .dev/services.sh
Add award service

@@ -12,6 +12,7 @@ SERVICES=(
   "post" # 8082
   "vote" # 8083
   "comment" # 8084
+  "award" # 8085
 )
 STARTING_PORT=8081
 

### 2023-05-25 api/src/main/award/router.py
Fix typo with STRIPE_ENDPOINT_SECRET

@@ -16,13 +16,13 @@ def webhook(request: Request, body: dict):
     event = None
     payload = body
 
-    if settings.EDNPOINT_SECRET:
+    if settings.STRIPE_ENDPOINT_SECRET:
         # Only verify the event if there is an endpoint secret defined
         # Otherwise use the basic event deserialized with json
         sig_header = request.headers['stripe-signature']
         try:
             event = stripe.Webhook.construct_event(
-                payload, sig_header, settings.EDNPOINT_SECRET
+                payload, sig_header, settings.STRIPE_ENDPOINT_SECRET
             )
         except stripe.error.SignatureVerificationError as e:
             print('⚠️  Webhook signature verification failed.' + str(e))

### 2023-05-25 api/src/main/award/settings.py

@@ -4,6 +4,7 @@ from src.main.shared.env import get_env
 class AwardServiceSettings:
     SERVICE_PREFIX: str = "/api/award"
     STRIPE_API_KEY = get_env("STRIPE_API_KEY")
+    STRIPE_ENDPOINT_SECRET = get_env("STRIPE_ENDPOINT_SECRET")
     STRIPE_SILVER_AWARD_PRICE = get_env("STRIPE_SILVER_AWARD_PRICE")
     STRIPE_GOLD_AWARD_PRICE = get_env("STRIPE_GOLD_AWARD_PRICE")
     STRIPE_PLATINUM_AWARD_PRICE = get_env("STRIPE_PLATINUM_AWARD_PRICE")

### 2023-05-25 api/src/main/award/router.py
Fix signature verification in webhooks

@@ -12,13 +12,11 @@ stripe.api_key = settings.STRIPE_API_KEY
 
 
 @router.post("/stripe_webhooks")
-def webhook(request: Request, body: dict):
+async def webhook(request: Request):
     event = None
-    payload = body
+    payload = await request.body()
 
     if settings.STRIPE_ENDPOINT_SECRET:
-        # Only verify the event if there is an endpoint secret defined
-        # Otherwise use the basic event deserialized with json
         sig_header = request.headers['stripe-signature']
         try:
             event = stripe.Webhook.construct_event(
@@ -28,19 +26,15 @@ def webhook(request: Request, body: dict):
             print('⚠️  Webhook signature verification failed.' + str(e))
             return {"success": False}
 
-        # Handle the event
-    if event and event['type'] == 'payment_intent.succeeded':
-        payment_intent = event['data']['object']  # contains a stripe.PaymentIntent
-        print('Payment for {} succeeded'.format(payment_intent['amount']))
-        # Then define and call a method to handle the successful payment intent.
-        # handle_payment_intent_succeeded(payment_intent)
-    elif event['type'] == 'payment_method.attached':
-        payment_method = event['data']['object']  # contains a stripe.PaymentMethod
-        # Then define and call a method to handle the successful attachment of a PaymentMethod.
-        # handle_payment_method_attached(payment_method)
+    event_type = event['type']
+    if event_type == 'checkout.session.completed':
+        print('checkout session completed')
+    elif event_type == 'invoice.paid':
+        print('invoice paid')
+    elif event_type == 'invoice.payment_failed':
+        print('invoice payment failed')
     else:
-        # Unexpected event type
-        print('Unhandled event type {}'.format(event['type']))
+        print(f'unhandled event: {event_type}')
 
     # Handle the event
     print('Handled event type {}'.format(event['type']))

### 2023-05-25 api/src/main/award/router.py
Make payment based on chosen award

@@ -1,9 +1,12 @@
+from typing import Annotated
+
 import stripe
 
-from fastapi import APIRouter, Request
+from fastapi import APIRouter, Request, Form
 from stripe.error import SignatureVerificationError
 from starlette.responses import RedirectResponse
 
+from src.main.award.util import determine_stripe_product
 from src.main.award.settings import settings
 
 router = APIRouter(prefix=settings.SERVICE_PREFIX)
@@ -43,12 +46,14 @@ async def webhook(request: Request):
 
 
 @router.post("/session")
-def create_checkout_session():
+def create_checkout_session(request: Request, subject_type: Annotated[str, Form()],
+                                              subject_id: Annotated[int, Form()],
+                                              award_type: Annotated[str, Form()]):
     try:
         checkout_session = stripe.checkout.Session.create(
             line_items=[
                 {
-                    'price': 'price_1NBcsqHMj8LggMg2UidsD64r',
+                    'price': determine_stripe_product(award_type),
                     'quantity': 1,
                 },
             ],

### 2023-05-25 api/src/main/award/util.py

@@ -1,0 +1,11 @@
+from src.main.award.settings import settings
+
+
+def determine_stripe_product(award_type: str):
+    match award_type:
+        case "silver":
+            return settings.STRIPE_SILVER_AWARD_PRICE
+        case "gold":
+            return settings.STRIPE_GOLD_AWARD_PRICE
+        case "platinum":
+            return settings.STRIPE_PLATINUM_AWARD_PRICE

### 2023-05-25 api/src/main/comment/model.py
Add awards columns

@@ -13,6 +13,9 @@ class Comment(Base):
     post_id = Column(Integer)
     commented_at = Column(DateTime(timezone=True), server_default=func.now())
     votes = Column(Integer, server_default="0")
+    silver_awards = Column(Integer, server_default="0")
+    gold_awards = Column(Integer, server_default="0")
+    platinum_awards = Column(Integer, server_default="0")
 
 
 class User(Base):

### 2023-05-25 api/src/main/post/model.py

@@ -14,6 +14,9 @@ class Post(Base):
     username = Column(String)
     post_type = Column(String)
     votes = Column(Integer, server_default="0")
+    silver_awards = Column(Integer, server_default="0")
+    gold_awards = Column(Integer, server_default="0")
+    platinum_awards = Column(Integer, server_default="0")
 
 
 class User(Base):

### 2023-05-25 api/src/main/shared/amqp/settings.py
Add exchanges for post and comment awards

@@ -13,8 +13,10 @@ class AmqpSettings(BaseSettings):
 
     # Exchanges
     AMQP_USER_REGISTERED_EXCHANGE_NAME: str = get_env("AMQP_USER_REGISTERED_EXCHANGE_NAME")
-    AMQP_POST_CREATED_EXCHANGE_NAME: str = get_env("AMQP_POST_CREATED_EXCHANGE_NAME")
-    AMQP_COMMENT_CREATED_EXCHANGE_NAME: str = get_env("AMQP_COMMENT_CREATED_EXCHANGE_NAME")
-    AMQP_POST_VOTE_CASTED_EXCHANGE_NAME: str = get_env("AMQP_POST_VOTE_CASTED_EXCHANGE_NAME")
-    AMQP_COMMENT_VOTE_CASTED_EXCHANGE_NAME: str = get_env("AMQP_COMMENT_VOTE_CASTED_EXCHANGE_NAME")
     AMQP_USER_DELETED_EXCHANGE_NAME: str = get_env("AMQP_USER_DELETED_EXCHANGE_NAME")
+    AMQP_POST_CREATED_EXCHANGE_NAME: str = get_env("AMQP_POST_CREATED_EXCHANGE_NAME")
+    AMQP_POST_VOTE_CASTED_EXCHANGE_NAME: str = get_env("AMQP_POST_VOTE_CASTED_EXCHANGE_NAME")
+    AMQP_POST_AWARDED_EXCHANGE_NAME = get_env("AMQP_POST_AWARDED_EXCHANGE_NAME")
+    AMQP_COMMENT_CREATED_EXCHANGE_NAME: str = get_env("AMQP_COMMENT_CREATED_EXCHANGE_NAME")
+    AMQP_COMMENT_VOTE_CASTED_EXCHANGE_NAME: str = get_env("AMQP_COMMENT_VOTE_CASTED_EXCHANGE_NAME")
+    AMQP_COMMENT_AWARDED_EXCHANGE_NAME = get_env("AMQP_COMMENT_AWARDED_EXCHANGE_NAME")

### 2023-05-25 api/src/main/award/lifespan.py
Make award service publisher for award events

@@ -1,0 +1,17 @@
+import asyncio
+from contextlib import asynccontextmanager
+
+from fastapi.applications import AppType
+from starlette.types import Lifespan
+
+from main.award.service import AwardService
+
+
+@asynccontextmanager
+async def lifespan(app: AwardService) -> Lifespan[AppType]:
+    loop = asyncio.get_running_loop()
+    task = loop.create_task(app.post_awarded_amqp_publisher.prepare_connection(loop))
+    await task
+    task = loop.create_task(app.comment_awarded_amqp_publisher.prepare_connection(loop))
+    await task
+    yield

### 2023-05-25 api/src/main/award/main.py

@@ -1,10 +1,11 @@
 from starlette.middleware.cors import CORSMiddleware
 
+from src.main.award.lifespan import lifespan
 from src.main.award.router import router
 from src.main.shared.cors.settings import settings as cors_settings
 from src.main.award.service import AwardService
 
-app = AwardService()
+app = AwardService(lifespan=lifespan)
 app.include_router(router)
 app.add_middleware(
     CORSMiddleware,

### 2023-05-25 api/src/main/award/service.py

@@ -1,6 +1,23 @@
 from fastapi import FastAPI
 
+from main.award.settings import settings
+from main.shared.amqp.amqp_publisher import AmqpPublisher
+
 
 class AwardService(FastAPI):
     def __init__(self, *args, **kwargs):
         super().__init__(*args, **kwargs)
+
+        self.post_awarded_amqp_publisher = None
+        self.comment_awarded_amqp_publisher = None
+        self.initialize_amqp_publishers()
+
+    def initialize_amqp_publishers(self):
+        self.post_awarded_amqp_publisher = AmqpPublisher(
+            settings.AMQP_URL,
+            exchange_name=settings.AMQP_POST_AWARDED_EXCHANGE_NAME
+        )
+        self.comment_awarded_amqp_publisher = AmqpPublisher(
+            settings.AMQP_URL,
+            exchange_name=settings.AMQP_COMMENT_AWARDED_EXCHANGE_NAME
+        )

### 2023-05-25 api/src/main/award/settings.py

@@ -1,7 +1,8 @@
+from src.main.shared.amqp.settings import AmqpSettings
 from src.main.shared.env import get_env
 
 
-class AwardServiceSettings:
+class AwardServiceSettings(AmqpSettings):
     SERVICE_PREFIX: str = "/api/award"
     STRIPE_API_KEY = get_env("STRIPE_API_KEY")
     STRIPE_ENDPOINT_SECRET = get_env("STRIPE_ENDPOINT_SECRET")

### 2023-05-25 api/src/main/award/router.py
Add metadata to stripe sessions

@@ -47,8 +47,8 @@ async def webhook(request: Request):
 
 @router.post("/session")
 def create_checkout_session(request: Request, subject_type: Annotated[str, Form()],
-                                              subject_id: Annotated[int, Form()],
-                                              award_type: Annotated[str, Form()]):
+                            subject_id: Annotated[int, Form()],
+                            award_type: Annotated[str, Form()]):
     try:
         checkout_session = stripe.checkout.Session.create(
             line_items=[
@@ -60,6 +60,11 @@ def create_checkout_session(request: Request, subject_type: Annotated[str, Form(
             mode='payment',
             success_url=settings.UI_URL + '/award?success=true',
             cancel_url=settings.UI_URL + '/award?canceled=true',
+            metadata={
+                'subject_type': subject_type,
+                'subject_id': subject_id,
+                'award_type': award_type
+            }
         )
         return RedirectResponse(url=checkout_session.url, status_code=303)
     except Exception as e:

### 2023-05-25 api/src/main/award/router.py
Shorten webhook endpoint

@@ -14,7 +14,7 @@ router = APIRouter(prefix=settings.SERVICE_PREFIX)
 stripe.api_key = settings.STRIPE_API_KEY
 
 
-@router.post("/stripe_webhooks")
+@router.post("/webhooks")
 async def webhook(request: Request):
     event = None
     payload = await request.body()

### 2023-05-25 api/src/main/award/router.py
Remove unused import

@@ -46,7 +46,7 @@ async def webhook(request: Request):
 
 
 @router.post("/session")
-def create_checkout_session(request: Request, subject_type: Annotated[str, Form()],
+def create_checkout_session(subject_type: Annotated[str, Form()],
                             subject_id: Annotated[int, Form()],
                             award_type: Annotated[str, Form()]):
     try:

### 2023-05-25 api/src/main/auth/router.py
Revert "Remove safeguards for testing"
This reverts commit 0c823001ca8be8cc478a5680c90d7c0290ff5518.

@@ -1,11 +1,12 @@
-from fastapi import APIRouter
+from fastapi import APIRouter, Depends
 from starlette.status import HTTP_202_ACCEPTED
 
 from src.main.auth.settings import settings
+from src.main.auth.util import azure_scheme
 
 router = APIRouter(prefix=settings.SERVICE_PREFIX)
 
 
-@router.get("", status_code=HTTP_202_ACCEPTED)
+@router.get("", status_code=HTTP_202_ACCEPTED, dependencies=[Depends(azure_scheme)])
 def authenticate():
-    return True
+    return None

### 2023-05-25 api/src/main/email/send_email.py

@@ -1,7 +1,39 @@
+from azure.communication.email import EmailClient
 from aio_pika.abc import AbstractIncomingMessage
 
+from src.main.email.settings import settings
+from src.main.email.util import construct_message
+from src.main.shared.amqp.amqp_util import decode_body_and_convert_to_dict
 from src.main.shared.logger import logger
+
+email_client = EmailClient.from_connection_string(settings.EMAIL_CONNECTION_STRING)
 
 
 def send_email(message: AbstractIncomingMessage) -> None:
-    logger.info("Sending email...")
+    body = decode_body_and_convert_to_dict(message.body)
+    recipients = body['recipients']
+    content_topic = body['content_topic']
+
+    try:
+        message = construct_message(recipients=recipients, content_topic=content_topic)
+        poller = email_client.begin_send(message)
+        time_elapsed = 0
+
+        while not poller.done():
+            logger.info(f"Email send poller status: {poller.status()}")
+
+            poller.wait(settings.POLLER_WAIT_TIME)
+            time_elapsed += settings.POLLER_WAIT_TIME
+
+            if time_elapsed > 18 * settings.POLLER_WAIT_TIME:
+                raise RuntimeError("Polling timed out.")
+
+        if poller.result()["status"] == "Succeeded":
+            logger.info(f"Successfully sent email (operation id: {poller.result()['id']})")
+        else:
+            raise RuntimeError(str(poller.result()["error"]))
+        logger.info("Result: ")
+        logger.info(poller.result())
+    except Exception as ex:
+        logger.error('Exception:')
+        logger.error(ex)

### 2023-05-25 api/src/main/vote/util.py

@@ -72,7 +72,11 @@ def assert_vote_exists(vote):
 
 
 def assert_vote_not_already_casted(db: Session, vote: dict):
-    crud.get_vote(db=db, target_id=vote["target_id"],
+    vote_already_casted = crud.get_vote(db=db, target_id=vote["target_id"],
                                         target_type=vote["target_type"],
                                         username=vote["username"]) is not None
-    return True
+    if vote_already_casted:
+        raise HTTPException(
+            status_code=HTTP_400_BAD_REQUEST,
+            detail=f"Vote already casted for this {vote['target_type']}"
+        )

### 2023-05-25 api/src/main/award/router.py
Remove explicit import

@@ -25,7 +25,7 @@ async def webhook(request: Request):
             event = stripe.Webhook.construct_event(
                 payload, sig_header, settings.STRIPE_ENDPOINT_SECRET
             )
-        except stripe.error.SignatureVerificationError as e:
+        except SignatureVerificationError as e:
             print('⚠️  Webhook signature verification failed.' + str(e))
             return {"success": False}
 

### 2023-05-25 docs/test/setup-testing-environment.sh
Resolve shellcheck warning

@@ -1,7 +1,7 @@
 #!/bin/sh
 # This script is expected to be run from root folder of repository.
 
-source ./.dev/util.sh
+. ./.dev/util.sh
 
 checkForVariable "JWT_TOKEN"
 checkForVariable "API_URL"

### 2023-05-26 api/src/main/award/lifespan.py
Fix wrong imports

@@ -4,7 +4,7 @@ from contextlib import asynccontextmanager
 from fastapi.applications import AppType
 from starlette.types import Lifespan
 
-from main.award.service import AwardService
+from src.main.award.service import AwardService
 
 
 @asynccontextmanager

### 2023-05-26 api/src/main/award/service.py

@@ -1,7 +1,7 @@
 from fastapi import FastAPI
 
-from main.award.settings import settings
-from main.shared.amqp.amqp_publisher import AmqpPublisher
+from src.main.award.settings import settings
+from src.main.shared.amqp.amqp_publisher import AmqpPublisher
 
 
 class AwardService(FastAPI):

### 2023-05-26 api/src/main/award/crud.py
Add awards to database and emit event on award payment

@@ -1,0 +1,22 @@
+from sqlalchemy.orm import Session
+
+from src.main.award.model import Award as AwardModel
+
+
+def create_award(db: Session, payment_intent: str, award_type: str, subject_type: str,
+                 subject_id: int, paid: bool = False):
+    db_award = AwardModel(payment_intent=payment_intent, award_type=award_type,
+                          subject_type=subject_type, subject_id=subject_id, paid=paid)
+    db.add(db_award)
+    db.commit()
+    db.refresh(db_award)
+
+
+def get_award_by_payment_intent(db: Session, payment_intent: str):
+    return db.query(AwardModel).filter(AwardModel.payment_intent == payment_intent).first()
+
+
+def set_award_to_paid(db: Session, award: AwardModel):
+    award.paid = True
+    db.commit()
+    db.refresh(award)

### 2023-05-26 api/src/main/award/lifespan.py

@@ -4,14 +4,20 @@ from contextlib import asynccontextmanager
 from fastapi.applications import AppType
 from starlette.types import Lifespan
 
+from src.main.shared.database.main import Base, engine
 from src.main.award.service import AwardService
 
 
 @asynccontextmanager
 async def lifespan(app: AwardService) -> Lifespan[AppType]:
+    create_database_tables()
     loop = asyncio.get_running_loop()
     task = loop.create_task(app.post_awarded_amqp_publisher.prepare_connection(loop))
     await task
     task = loop.create_task(app.comment_awarded_amqp_publisher.prepare_connection(loop))
     await task
     yield
+
+
+def create_database_tables():
+    Base.metadata.create_all(bind=engine)

### 2023-05-26 api/src/main/award/model.py

@@ -1,0 +1,14 @@
+from sqlalchemy import Column, String, Integer, Boolean
+
+from src.main.shared.database.main import Base
+
+
+class Award(Base):
+    __tablename__ = "awards"
+
+    id = Column(Integer, primary_key=True, index=True)
+    award_type = Column(String)
+    subject_type = Column(String)
+    subject_id = Column(Integer)
+    payment_intent = Column(String, unique=True)
+    paid = Column(Boolean, default=False)

### 2023-05-26 api/src/main/award/router.py

@@ -2,11 +2,14 @@ from typing import Annotated
 
 import stripe
 
-from fastapi import APIRouter, Request, Form
+from fastapi import APIRouter, Request, Form, BackgroundTasks, Depends
+from sqlalchemy.orm import Session
 from stripe.error import SignatureVerificationError
 from starlette.responses import RedirectResponse
 
-from src.main.award.util import determine_stripe_product
+from src.main.shared.database.main import get_db
+from src.main.award import crud
+from src.main.award.util import determine_stripe_product, emit_award_given_event
 from src.main.award.settings import settings
 
 router = APIRouter(prefix=settings.SERVICE_PREFIX)
@@ -15,7 +18,8 @@ stripe.api_key = settings.STRIPE_API_KEY
 
 
 @router.post("/webhooks")
-async def webhook(request: Request):
+async def webhook(request: Request, background_tasks: BackgroundTasks,
+                  db: Session = Depends(get_db)):
     event = None
     payload = await request.body()
 
@@ -30,17 +34,18 @@ async def webhook(request: Request):
             return {"success": False}
 
     event_type = event['type']
-    if event_type == 'checkout.session.completed':
-        print('checkout session completed')
-    elif event_type == 'invoice.paid':
-        print('invoice paid')
-    elif event_type == 'invoice.payment_failed':
-        print('invoice payment failed')
-    else:
-        print(f'unhandled event: {event_type}')
-
-    # Handle the event
-    print('Handled event type {}'.format(event['type']))
+    if event_type == "checkout.session.completed":
+        metadata = event['data']['object']['metadata']
+        payment_intent = event['data']['object']['payment_intent']
+        crud.create_award(
+            db=db, payment_intent=payment_intent, award_type=metadata['award_type'],
+            subject_type=metadata['subject_type'], subject_id=metadata['subject_id']
+        )
+    elif event_type == "payment_intent.succeeded":
+        payment_intent = event['data']['object']['id']
+        award = crud.get_award_by_payment_intent(db=db, payment_intent=payment_intent)
+        crud.set_award_to_paid(db=db, award=award)
+        background_tasks.add_task(emit_award_given_event, request=request, award=award)
 
     return {"success": True}
 
@@ -50,6 +55,7 @@ def create_checkout_session(subject_type: Annotated[str, Form()],
                             subject_id: Annotated[int, Form()],
                             award_type: Annotated[str, Form()]):
     try:
[…]

### 2023-05-26 api/src/main/award/util.py

@@ -1,3 +1,8 @@
+import json
+from fastapi import Request
+
+from src.main.award.model import Award as AwardModel
+
 from src.main.award.settings import settings
 
 
@@ -9,3 +14,14 @@ def determine_stripe_product(award_type: str):
             return settings.STRIPE_GOLD_AWARD_PRICE
         case "platinum":
             return settings.STRIPE_PLATINUM_AWARD_PRICE
+
+
+async def emit_award_given_event(request: Request, award: AwardModel):
+    body = json.dumps({
+        "award_type": award.award_type,
+        "subject_id": award.subject_id,
+    })
+    if award.subject_type == "post":
+        await request.app.post_awarded_amqp_publisher.send_message(str(body))
+    elif award.subject_type == "comment":
+        await request.app.comment_awarded_amqp_publisher.send_message(str(body))

### 2023-05-26 api/src/main/post/crud.py
Update awards fields on awarded post

@@ -44,6 +44,27 @@ def update_post_body(db: Session, post_id: int, body: str):
     return db_post
 
 
+def update_post_silver_awards(db: Session, post_id: int):
+    db_post = db.query(PostModel).filter(PostModel.id == post_id).first()
+    db_post.silver_awards += 1
+    db.commit()
+    db.refresh(db_post)
+
+
+def update_post_gold_awards(db: Session, post_id: int):
+    db_post = db.query(PostModel).filter(PostModel.id == post_id).first()
+    db_post.gold_awards += 1
+    db.commit()
+    db.refresh(db_post)
+
+
+def update_post_platinum_awards(db: Session, post_id: int):
+    db_post = db.query(PostModel).filter(PostModel.id == post_id).first()
+    db_post.platinum_awards += 1
+    db.commit()
+    db.refresh(db_post)
+
+
 def cast_upvote(db: Session, post_id: int):
     db_post = db.query(PostModel).filter(PostModel.id == post_id).first()
     db_post.votes += 1

### 2023-05-26 api/src/main/post/lifespan.py

@@ -21,6 +21,8 @@ async def lifespan(app: PostService) -> Lifespan[AppType]:
     await task
     task = loop.create_task(app.user_deleted_amqp_consumer.consume(loop))
     await task
+    task = loop.create_task(app.post_awarded_amqp_consumer.consume(loop))
+    await task
     yield
 
 

### 2023-05-26 api/src/main/post/service.py

@@ -3,7 +3,8 @@ from fastapi import FastAPI
 from src.main.shared.amqp.amqp_consumer import AmqpConsumer
 from src.main.shared.amqp.amqp_publisher import AmqpPublisher
 from src.main.post.settings import settings
-from src.main.post.util import handle_user_registration, handle_vote_casted, handle_user_deleted
+from src.main.post.util import handle_user_registration, handle_vote_casted, handle_user_deleted, \
+    handle_post_awarded
 
 
 class PostService(FastAPI):
@@ -13,6 +14,7 @@ class PostService(FastAPI):
         self.user_registered_amqp_consumer = None
         self.post_vote_casted_amqp_consumer = None
         self.user_deleted_amqp_consumer = None
+        self.post_awarded_amqp_consumer = None
         self.initialize_amqp_consumers()
 
         self.post_created_amqp_publisher = None
@@ -36,6 +38,12 @@ class PostService(FastAPI):
             exchange_name=settings.AMQP_USER_DELETED_EXCHANGE_NAME,
             queue_name=settings.AMQP_USER_DELETED_QUEUE_NAME,
             incoming_message_handler=handle_user_deleted,
+        )
+        self.post_awarded_amqp_consumer = AmqpConsumer(
+            settings.AMQP_URL,
+            exchange_name=settings.AMQP_POST_AWARDED_EXCHANGE_NAME,
+            queue_name=settings.AMQP_POST_AWARDED_QUEUE_NAME,
+            incoming_message_handler=handle_post_awarded,
         )
 
     def initialize_amqp_publishers(self):

### 2023-05-26 api/src/main/post/settings.py

@@ -8,6 +8,7 @@ class PostServiceSettings(AmqpSettings):
     AMQP_USER_REGISTERED_QUEUE_NAME: str = "post_service_user_registered_queue"
     AMQP_POST_VOTE_CASTED_QUEUE_NAME: str = "post_service_post_vote_casted_queue"
     AMQP_USER_DELETED_QUEUE_NAME: str = "post_service_user_deleted_queue"
+    AMQP_POST_AWARDED_QUEUE_NAME: str = "post_service_post_awarded_queue"
     # Azure Blob Storage
     BLOB_STORAGE_ACCOUNT_NAME: str = get_env("BLOB_STORAGE_ACCOUNT_NAME")
     BLOB_STORAGE_CONNECTION_STRING: str = get_env("BLOB_STORAGE_CONNECTION_STRING")

### 2023-05-26 api/src/main/post/util.py

@@ -80,6 +80,19 @@ def handle_user_registration(message: AbstractIncomingMessage) -> None:
     crud.insert_user(db=db, username=username, oid=oid)
 
 
+def handle_post_awarded(message: AbstractIncomingMessage) -> None:
+    body = decode_body_and_convert_to_dict(message.body)
+    post_id = body['subject_id']
+    db = next(get_db())
+    award_type = body['award_type']
+    if award_type == "silver":
+        crud.update_post_silver_awards(db=db, post_id=post_id)
+    elif award_type == "gold":
+        crud.update_post_gold_awards(db=db, post_id=post_id)
+    elif award_type == "platinum":
+        crud.update_post_platinum_awards(db=db, post_id=post_id)
+
+
 def assert_user_is_owner_of_post(db: Session, request: Request, post_id: int):
     oid = get_access_token_oid(request=request)
     username = crud.get_username_by_oid(db=db, oid=oid)

### 2023-05-26 api/src/main/comment/crud.py
Update awards fields on awarded comment

@@ -37,6 +37,27 @@ def create_comment(db: Session, comment: dict):
     return db_comment
 
 
+def update_comment_silver_awards(db: Session, comment_id: int):
+    db_comment = db.query(CommentModel).filter(CommentModel.id == comment_id).first()
+    db_comment.silver_awards += 1
+    db.commit()
+    db.refresh(db_comment)
+
+
+def update_comment_gold_awards(db: Session, comment_id: int):
+    db_comment = db.query(CommentModel).filter(CommentModel.id == comment_id).first()
+    db_comment.gold_awards += 1
+    db.commit()
+    db.refresh(db_comment)
+
+
+def update_comment_platinum_awards(db: Session, comment_id: int):
+    db_comment = db.query(CommentModel).filter(CommentModel.id == comment_id).first()
+    db_comment.platinum_awards += 1
+    db.commit()
+    db.refresh(db_comment)
+
+
 def delete_user_comments(db: Session, username: str):
     db.query(CommentModel).filter(CommentModel.username == username).delete()
     db.commit()
@@ -44,17 +65,17 @@ def delete_user_comments(db: Session, username: str):
 
 
 def cast_upvote(db: Session, comment_id: int):
-    db_post = db.query(CommentModel).filter(CommentModel.id == comment_id).first()
-    db_post.votes += 1
+    db_comment = db.query(CommentModel).filter(CommentModel.id == comment_id).first()
+    db_comment.votes += 1
     db.commit()
-    db.refresh(db_post)
+    db.refresh(db_comment)
 
 
 def cast_downvote(db: Session, comment_id: int):
-    db_post = db.query(CommentModel).filter(CommentModel.id == comment_id).first()
-    db_post.votes -= 1
+    db_comment = db.query(CommentModel).filter(CommentModel.id == comment_id).first()
+    db_comment.votes -= 1
     db.commit()
-    db.refresh(db_post)
+    db.refresh(db_comment)
 
 
 def delete_comment(db: Session, comment_id: int):

### 2023-05-26 api/src/main/comment/lifespan.py

@@ -21,6 +21,8 @@ async def lifespan(app: CommentService) -> Lifespan[AppType]:
     await task
     task = loop.create_task(app.user_deleted_amqp_consumer.consume(loop))
     await task
+    task = loop.create_task(app.comment_awarded_amqp_consumer.consume(loop))
+    await task
     yield
 
 

### 2023-05-26 api/src/main/comment/service.py

@@ -3,7 +3,7 @@ from fastapi import FastAPI
 from src.main.shared.amqp.amqp_consumer import AmqpConsumer
 from src.main.comment.settings import settings
 from src.main.comment.util import handle_user_registration, handle_post_creation, \
-    handle_vote_casted, handle_user_deleted
+    handle_vote_casted, handle_user_deleted, handle_comment_awarded
 from src.main.shared.amqp.amqp_publisher import AmqpPublisher
 
 
@@ -15,6 +15,7 @@ class CommentService(FastAPI):
         self.post_created_amqp_consumer = None
         self.comment_vote_casted_amqp_consumer = None
         self.user_deleted_amqp_consumer = None
+        self.comment_awarded_amqp_consumer = None
         self.initialize_amqp_consumers()
 
         self.comment_created_amqp_publisher = None
@@ -44,6 +45,12 @@ class CommentService(FastAPI):
             exchange_name=settings.AMQP_USER_DELETED_EXCHANGE_NAME,
             queue_name=settings.AMQP_USER_DELETED_QUEUE_NAME,
             incoming_message_handler=handle_user_deleted,
+        )
+        self.comment_awarded_amqp_consumer = AmqpConsumer(
+            settings.AMQP_URL,
+            exchange_name=settings.AMQP_COMMENT_AWARDED_EXCHANGE_NAME,
+            queue_name=settings.AMQP_COMMENT_AWARDED_QUEUE_NAME,
+            incoming_message_handler=handle_comment_awarded,
         )
 
     def initialize_amqp_publishers(self):

### 2023-05-26 api/src/main/comment/settings.py

@@ -7,6 +7,7 @@ class CommentServiceSettings(AmqpSettings):
     AMQP_POST_CREATED_QUEUE_NAME: str = "comment_service_post_created_queue"
     AMQP_COMMENT_VOTE_CASTED_QUEUE_NAME: str = "comment_service_comment_vote_casted_queue"
     AMQP_USER_DELETED_QUEUE_NAME: str = "comment_service_user_deleted_queue"
+    AMQP_COMMENT_AWARDED_QUEUE_NAME: str = "comment_service_comment_awarded_queue"
 
 
 settings = CommentServiceSettings()

### 2023-05-26 api/src/main/comment/util.py

@@ -39,6 +39,19 @@ def handle_vote_casted(message: AbstractIncomingMessage):
         crud.cast_downvote(db=db, comment_id=body["comment_id"])
 
 
+def handle_comment_awarded(message: AbstractIncomingMessage):
+    body = decode_body_and_convert_to_dict(message.body)
+    comment_id = body['subject_id']
+    db = next(get_db())
+    award_type = body['award_type']
+    if award_type == "silver":
+        crud.update_comment_silver_awards(db=db, comment_id=comment_id)
+    elif award_type == "gold":
+        crud.update_comment_gold_awards(db=db, comment_id=comment_id)
+    elif award_type == "platinum":
+        crud.update_comment_platinum_awards(db=db, comment_id=comment_id)
+
+
 def handle_user_deleted(message: AbstractIncomingMessage):
     body = decode_body_and_convert_to_dict(message.body)
     db = next(get_db())

### 2023-06-08 docs/research/LaTeX/research.tex
Add research folder with data

\documentclass[12pt, a4paper]{article}
\usepackage{indentfirst}
\usepackage{graphicx}
\graphicspath{{images/}}
\title{GDPR: Is non-compliance profitable for Meta Platforms, Inc.?}
\author{Stoyan L. Kostadinov}
\date{June 2023}
\begin{document}
\maketitle

\begin{center}
    \includegraphics[width=0.3\textwidth]{fontys-logo}
\end{center}

\begin{abstract}
    % TODO
\end{abstract}

\subsection*{Keywords}

GDPR, Facebook, Meta, profit, non-compliance, big tech, privacy

\section*{Introduction}

In the recent years, the increasing usage of the Internet has lead to a rapid
expansion of data collection and processing\cite{}. As concerns regarding data
privacy and protection grew, the European Union (EU) implemented the General
Data Protection Regulation (GDPR) in May 2018\cite{}.

GDPR aimed to safeguard the privacy rights of individuals within the EU by
regulating the collection, storage, and transfer of personal data\cite{}.
Notably, data should be collected for specified, explicit and legitimate
purposes\cite{} and data can be transferred outside the EU if general data
processing principles are in place \cite{}. Compliance with GDPR has become a
critical issue for big-tech companies, which often handle massive amounts of
user data.

One of those companies is \textit{Meta Platforms, Inc.} (formerly
\textit{Facebook, Inc.}), which has been fined numerous times for GDPR
violations and amounts for more than half of the total currency value of all
GDPR fines\cite{}. The company has also faced legal challenges and public
backlash over its data collection practices\cite{}. This has raised questions
about the financial impact of GDPR non-compliance on \textit{Meta Platforms,
Inc.} and whether it is profitable for the company to continue violating the
regulation.

\section*{Method}

Most of the numerical data is coming from the Meta Investor Relations
website\cite{}.

This research is also following the protocol of Prisma flowchart for systematic
reviews\cite{}. Google Scholar was used to search for articles containing the
keywords above. The first 360 results were considered. The articles were
filtered by relevance following their titles and 60 were considered. The
abstracts of the 60 articles were read and X were considered
% TODO: Describe flowchart with sentences above here TODO: Put numbers and add
% flowchart here as Figure 1

\subsection*{Inclusion criteria}

\begin{itemize}
    \item Articles published in English
    \item Articles published between 2018 and 2023
    \item Articles that discuss GDPR
    \item Articles that discuss Meta Platforms, Inc.
    \item Articles that discuss the profit of Meta Platforms, Inc.
    \item Articles that discuss the non-compliance of Meta Platforms, Inc.
\end{itemize}

\subsection*{Exclusion criteria}

\begin{itemize}
    \item Articles published in languages other than English
    \item Articles published before 2018
    \item Articles that do not discuss GDPR
    \item Articles that do not discuss Meta Platforms, Inc.
    \item Articles that discuss about ethics
    \item Articles that discuss about the impact of GDPR
    \item Articles that discuss about the impact of Meta Platforms, Inc.
\end{itemize}

\subsection*{Ethical considerations}

This study is approved by Fontys University of Applied Sciences, Eindhoven, The
Netherlands. All data is collected from publicly available sources and no
personal data is collected. The author is not affiliated with Meta Platforms,
Inc. or any other company mentioned in this study.

\section*{Results}

\subsection*{Fines analysis}

%Explore the fines imposed on Meta Platforms by regulatory authorities due to
%GDPR violations. Examine the magnitude of the fines, both in absolute terms and
%in relation to the company's financial performance. Compare the fines to Meta
%Platforms' revenue, profits, or other financial indicators to assess their
%significance.

\subsection*{Legal expenses}

% Investigate the costs incurred by Meta Platforms in legal proceedings related
% to GDPR non-compliance. This includes expenses associated with hiring legal
% counsel, litigation, settlement agreements, and any ongoing legal obligations.
% Analyze the financial impact of these legal expenses on the company's
% profitability.

\subsection*{Investor Confidence and Stock Performance}

% Assess the impact of GDPR non-compliance on Meta Platforms' stock performance.
% Analyze stock price movements, market reactions to GDPR-related news, and
% changes in investor sentiment. Explore how GDPR issues have influenced
% investor confidence and the company's market capitalization.

\subsection*{Advertiser Reactions}

% Study the response of advertisers to GDPR non-compliance by Meta Platforms.
% Examine whether there has been a shift in advertiser behavior, such as reduced
% advertising spend, contract cancellations, or demands for stricter data
% protection measures. Analyze the financial implications of these reactions on
% Meta Platforms' advertising revenue.

\subsection*{User Base and User Engagement}

% Investigate whether GDPR non-compliance has had any impact on Meta Platforms'
% user base and user engagement metrics. Analyze changes in user growth rates,
% active user counts, or user activity patterns following GDPR-related
% incidents. Assess the potential financial consequences of any decline in user
% metrics.

\subsection*{Reputational Damage}

% Assess the financial impact of reputational damage resulting from GDPR
% non-compliance. Investigate whether negative media coverage, public backlash,
% or loss of user trust have affected Meta Platforms' brand value or customer
% perception. Analyze any associated costs, such as brand recovery campaigns or
% decreased user acquisition rates.

\bibliographystyle{vancouver}
\bibliography{refs}
\end{document}

### 2023-06-08 docs/research/transform_enforcementtracker_gdpr_fines.sh
Add script for transforming data of gdpr fines

@@ -1,0 +1,25 @@
+#!/bin/bash
+
+
+JSON_FILE=$1
+echo "JSON_FILE: $JSON_FILE"
+if [[ -z $1 ]]; then
+  echo "JSON file is required"
+  echo "Usage: $BASH_SOURCE <JSON file>"
+  exit 1
+fi
+
+echo "Removing <img> tags"
+sed -i "s/<img[^>]*>//g" "$JSON_FILE"
+
+echo "Removing first item in each array"
+jq 'del(.data[][] | select(. == ""))' "$JSON_FILE" | sponge "$JSON_FILE"
+
+echo "Converting all to objects"
+jq '.data[] | {id: .[0], country: .[1], authority: .[2], date: .[3], fine: .[4], sector: .[5], category: .[6], article: .[7], violation: .[8], summary: .[9], link: .[10], enforcement: .[11]}' "$JSON_FILE" | sponge "$JSON_FILE"
+
+echo "Converting file to JSON"
+jq -s '.' "$JSON_FILE" | sponge "$JSON_FILE"
+
+echo "Removing <br> tags"
+sed -i "s/<br \/>//g" "$JSON_FILE"

### 2023-06-08 docs/research/extract_meta_related_fines.sh
Extract meta fines

@@ -1,0 +1,16 @@
+#!/bin/bash
+
+JSON_FILE=$1
+NEW_FILE=$2
+echo "JSON_FILE: $JSON_FILE"
+if [[ -z $1 || -z $2 ]]; then
+  echo "JSON file is required"
+  echo "Usage: ${BASH_SOURCE[0]} <JSON file> <NEW File>"
+  exit 1
+fi
+
+jq '.[] | select(.controller | test("(Meta|Facebook|WhatsApp|Instagram)"; "i"))' "$JSON_FILE" | sponge "$NEW_FILE"
+
+echo "Converting $NEW_FILE file to JSON"
+jq -s '.' "$NEW_FILE" | sponge "$NEW_FILE"
+echo "There could be some false positives. Check file manually."

### 2023-06-08 docs/research/transform_enforcementtracker_gdpr_fines.sh

@@ -5,7 +5,7 @@ JSON_FILE=$1
 echo "JSON_FILE: $JSON_FILE"
 if [[ -z $1 ]]; then
   echo "JSON file is required"
-  echo "Usage: $BASH_SOURCE <JSON file>"
+  echo "Usage: ${BASH_SOURCE[0]} <JSON file>"
   exit 1
 fi
 
@@ -16,7 +16,7 @@ echo "Removing first item in each array"
 jq 'del(.data[][] | select(. == ""))' "$JSON_FILE" | sponge "$JSON_FILE"
 
 echo "Converting all to objects"
-jq '.data[] | {id: .[0], country: .[1], authority: .[2], date: .[3], fine: .[4], sector: .[5], category: .[6], article: .[7], violation: .[8], summary: .[9], link: .[10], enforcement: .[11]}' "$JSON_FILE" | sponge "$JSON_FILE"
+jq '.data[] | {id: .[0], country: .[1], authority: .[2], date: .[3], fine: .[4], controller: .[5], category: .[6], article: .[7], violation: .[8], summary: .[9], link: .[10], enforcement: .[11]}' "$JSON_FILE" | sponge "$JSON_FILE"
 
 echo "Converting file to JSON"
 jq -s '.' "$JSON_FILE" | sponge "$JSON_FILE"

### 2023-06-09 docs/research/LaTeX/research.tex
Add script for transforming data of gdpr fines
Finish research introduction

@@
 \usepackage{graphicx}
+\usepackage{url}
 \graphicspath{{images/}}
@@
 
-GDPR, Facebook, Meta, profit, non-compliance, big tech, privacy
+GDPR, Facebook, Meta, profit, non-compliance, big tech, privacy, financial
+impact
 
@@
 In the recent years, the increasing usage of the Internet has lead to a rapid
-expansion of data collection and processing\cite{}. As concerns regarding data
-privacy and protection grew, the European Union (EU) implemented the General
-Data Protection Regulation (GDPR) in May 2018\cite{}.
+expansion of data collection and processing\cite{khan2014big}. As concerns
+regarding data privacy and protection grew, the European Union (EU) implemented
+the General Data Protection Regulation (GDPR) in May
+2018\cite{greengard2018weighing, historyGdpr}.
 
 GDPR aimed to safeguard the privacy rights of individuals within the EU by
-regulating the collection, storage, and transfer of personal data\cite{}.
-Notably, data should be collected for specified, explicit and legitimate
-purposes\cite{} and data can be transferred outside the EU if general data
-processing principles are in place \cite{}. Compliance with GDPR has become a
+regulating the collection, storage, and transfer of personal
+data\cite{historyGdpr}. Notably, data should be collected for specified,
+explicit and legitimate purposes\cite{europeanParliamentGdprArticle5} and data
+can be transferred outside the EU if general data processing principles are in
+place \cite{europeanParliamentGdprArticle44}. Compliance with GDPR has become a
 critical issue for big-tech companies, which often handle massive amounts of
@@
 \textit{Facebook, Inc.}), which has been fined numerous times for GDPR
-violations and amounts for more than half of the total currency value of all
-GDPR fines\cite{}. The company has also faced legal challenges and public
-backlash over its data collection practices\cite{}. This has raised questions
-about the financial impact of GDPR non-compliance on \textit{Meta Platforms,
-Inc.} and whether it is profitable for the company to continue violating the
-regulation.
+violations\cite{mrevzar2023analysis}. This has raised questions about the
+financial impact of GDPR non-compliance from \textit{Meta} and whether it is
+profitable for the company to continue violating the regulation.
+
+The goal of this paper is to investigate the financial impact of GDPR
+non-compliance on \textit{Meta Platforms, Inc.} and to determine whether it is
+profitable for the company to continue violating the regulations.
 
@@
 
-Most of the numerical data is coming from the Meta Investor Relations
-website\cite{}.
+All numerical data about \textit{Meta Platforms, Inc.} has been gathered from
+the official \textit{Meta Investor Relations} website\cite{fbMetaFinancials}.
 
-This research is also following the protocol of Prisma flowchart for systematic
-reviews\cite{}. Google Scholar was used to search for articles containing the
-keywords above. The first 360 results were considered. The articles were
-filtered by relevance following their titles and 60 were considered. The
-abstracts of the 60 articles were read and X were considered
+GDPR fines imposed on \textit{Meta Platforms, Inc.} have been gathered from the
+\textit{GDPR Enforcement Tracker}
+website\cite{enforcementtrackerGDPREnforcement}.
+
+This research is following the protocol of \textit{Prisma flowchart} for
+systematic reviews\cite{prismaFlowchart}.
+
+\textit{Google Scholar} was used to search for articles containing the keywords
+above. The first 360 results were considered. The articles were filtered by
+relevance following their titles and 60 were considered. The abstracts of the 60
+articles were read and X were considered
 % TODO: Describe flowchart with sentences above here TODO: Put numbers and add
@@
     \item Articles that discuss Meta Platforms, Inc.
-    \item Articles that discuss the profit of Meta Platforms, Inc.
-    \item Articles that discuss the non-compliance of Meta Platforms, Inc.
+    \item Data between 2021 and 2023
 \end{itemize}
@@
     \item Articles that discuss about ethics
-    \item Articles that discuss about the impact of GDPR
-    \item Articles that discuss about the impact of Meta Platforms, Inc.
+    \item Data before 2021
 \end{itemize}

### 2023-06-10 docs/research/LaTeX/research.tex
Add first 3 figures and edit method

@@
 \usepackage{url}
+\usepackage[font=footnotesize,labelfont=bf]{caption}
 \graphicspath{{images/}}
@@
 
-GDPR, Facebook, Meta, profit, non-compliance, big tech, privacy, financial
-impact
+GDPR, Facebook, Meta, profit, non-compliance, privacy, financial impact
 
@@
 \textit{Facebook, Inc.}), which has been fined numerous times for GDPR
-violations\cite{mrevzar2023analysis}. This has raised questions about the
-financial impact of GDPR non-compliance from \textit{Meta} and whether it is
-profitable for the company to continue violating the regulation.
+violations\cite{mrevzar2023analysis}. This has raised questions about the impact
+of GDPR on \textit{Meta's} performance.
 
@@
 All numerical data about \textit{Meta Platforms, Inc.} has been gathered from
-the official \textit{Meta Investor Relations} website\cite{fbMetaFinancials}.
+the official \textit{Meta Investor Relations} website\cite{fbMetaFinancials} -
+\textbf{Balance Sheet}, \textbf{Income Statement} and \textbf{Form 10-Q}.
 
@@
 \textit{GDPR Enforcement Tracker}
-website\cite{enforcementtrackerGDPREnforcement}.
-
-This research is following the protocol of \textit{Prisma flowchart} for
-systematic reviews\cite{prismaFlowchart}.
-
-\textit{Google Scholar} was used to search for articles containing the keywords
-above. The first 360 results were considered. The articles were filtered by
-relevance following their titles and 60 were considered. The abstracts of the 60
-articles were read and X were considered
-% TODO: Describe flowchart with sentences above here TODO: Put numbers and add
-% flowchart here as Figure 1
+website\cite{enforcementtrackerGDPREnforcement} and filtered to include fines
+imposed on their family of applications (\textbf{\textit{Facebook}},
+\textbf{\textit{WhatsApp}}, \textbf{\textit{Instagram}}) and
+\textbf{\textit{Meta Platforms, Inc.}} itself.
 
@@
     \item Articles that discuss Meta Platforms, Inc.
-    \item Data between 2021 and 2023
+    \item Data between 2018 and 2023
 \end{itemize}
@@
     \item Articles that discuss about ethics
-    \item Data before 2021
+    \item Data before 2018
 \end{itemize}
@@
 
+% TODO: cite
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1.00\textwidth]{monetarial-amount-of-gdpr-fines}
+    \caption{Monetarial amount of fines issued to Meta Platforms, Inc.(in millions of \$)}
+    \label{fig:amount-of-gdpr-fines}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1.00\textwidth]{violations-by-article}
+    \caption{Number of violations by GDPR article}
+    \label{fig:violations-by-article}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1.00\textwidth]{net-income}
+    \caption{Net Income of Meta Platforms, Inc.(in billions of \$)}
+    \label{fig:net-income}
+\end{figure}
+
 \subsection*{Legal expenses}
@@
 % profitability.
+% https://www.law.com/corpcounsel/2021/11/24/as-regulators-hover-meta-expands-legal-department/
+
+% https://www.law.com/corpcounsel/2022/11/10/meta-cuts-hit-legal-department-slamming-brakes-on-its-explosive-growth/?slreturn=20230510140111
+
+% https://www.google.com/search?channel=fs&client=ubuntu&q=glasdoor+meta+lawyer+salary
 
@@
 
+% advertising data
+
 \subsection*{User Base and User Engagement}
@@
 % metrics.
+
+% https://d18rn0p25nwr6d.cloudfront.net/CIK-0001326801/5fb5d0ea-c2c7-46f0-a26a-656df1673fac.pdf
+% page 14 revenue from europe page 42 41 37 and onwards
 
@@
 
+% hard to assess
+
 \bibliographystyle{vancouver}

### 2023-06-11 docs/research/LaTeX/research.tex
Add 4 charts

@@
 \usepackage{url}
+\usepackage{cite}
 \usepackage[font=footnotesize,labelfont=bf]{caption}
@@
 the official \textit{Meta Investor Relations} website\cite{fbMetaFinancials} -
-\textbf{Balance Sheet}, \textbf{Income Statement} and \textbf{Form 10-Q}.
+\textbf{Balance Sheets}, \textbf{Income Statements} and \textbf{Form 10-Q}.
 
@@
     \includegraphics[width=1.00\textwidth]{monetarial-amount-of-gdpr-fines}
-    \caption{Monetarial amount of fines issued to Meta Platforms, Inc.(in millions of \$)}
+    \caption{Monetarial amount of fines issued to Meta Platforms, Inc.(in
+    millions of
+    \$)\cite{gdprFine1,gdprFine2,gdprFine3,gdprFine4,gdprFine5,gdprFine6,gdprFine7,gdprFine8,gdprFine9}}
     \label{fig:amount-of-gdpr-fines}
@@
     \includegraphics[width=1.00\textwidth]{violations-by-article}
-    \caption{Number of violations by GDPR article}
+    \caption{Number of violations by GDPR
+    article\cite{gdprFine1,gdprFine2,gdprFine3,gdprFine4,gdprFine5,gdprFine6,gdprFine7,gdprFine8,gdprFine9}}
     \label{fig:violations-by-article}
@@
     \includegraphics[width=1.00\textwidth]{net-income}
-    \caption{Net Income of Meta Platforms, Inc.(in billions of \$)}
+    \caption{Net Income of Meta Platforms, Inc.(in billions of
+    \$)\cite{2023q1,2020q4,2020q3,2020q2,2020q1,2019q4,2019q3,2019q2,2019q1,2018q4,2018q3,2018q2}}
     \label{fig:net-income}
@@
 
-\subsection*{Legal expenses}
-
-% Investigate the costs incurred by Meta Platforms in legal proceedings related
-% to GDPR non-compliance. This includes expenses associated with hiring legal
-% counsel, litigation, settlement agreements, and any ongoing legal obligations.
-% Analyze the financial impact of these legal expenses on the company's
-% profitability.
-% https://www.law.com/corpcounsel/2021/11/24/as-regulators-hover-meta-expands-legal-department/
-
-% https://www.law.com/corpcounsel/2022/11/10/meta-cuts-hit-legal-department-slamming-brakes-on-its-explosive-growth/?slreturn=20230510140111
-
-% https://www.google.com/search?channel=fs&client=ubuntu&q=glasdoor+meta+lawyer+salary
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1.00\textwidth]{revenue}
+    \caption{Revenue of Meta Platforms, Inc.(in billions of
+    \$)\cite{2023q1,2020q4,2020q3,2020q2,2020q1,2019q4,2019q3,2019q2,2019q1,2018q4,2018q3,2018q2}}
+    \label{fig:revenue}
+\end{figure}
 
@@
 
-% advertising data
+% Average revenue per person Trends in Our Monetization by Facebook User
+% Geography page 46 - advertising
 
@@
 
+% Daily Active People Monthly Active People Daily Active Users (DAUs) facebook -
+% per region Monthly Active Users (MAUs) facebook - per region
+
 % https://d18rn0p25nwr6d.cloudfront.net/CIK-0001326801/5fb5d0ea-c2c7-46f0-a26a-656df1673fac.pdf
@@
 
-\subsection*{Reputational Damage}
+\section{Discussion}
 
-% Assess the financial impact of reputational damage resulting from GDPR
-% non-compliance. Investigate whether negative media coverage, public backlash,
-% or loss of user trust have affected Meta Platforms' brand value or customer
-% perception. Analyze any associated costs, such as brand recovery campaigns or
-% decreased user acquisition rates.
+% % Investigate the costs incurred by Meta Platforms in legal proceedings
+% related to GDPR non-compliance. This includes expenses associated with hiring
+% legal counsel, litigation, settlement agreements, and any ongoing legal
+% obligations. Analyze the financial impact of these legal expenses on the
+% company's profitability. Reputational Damage Assess the financial impact of
+% reputational damage resulting from GDPR non-compliance. Investigate whether
+% negative media coverage, public backlash, or loss of user trust have affected
+% Meta Platforms' brand value or customer perception. Analyze any associated
+% costs, such as brand recovery campaigns or decreased user acquisition rates.
 
 % hard to assess
+
+% https://www.law.com/corpcounsel/2021/11/24/as-regulators-hover-meta-expands-legal-department/
+
+% https://www.law.com/corpcounsel/2022/11/10/meta-cuts-hit-legal-department-slamming-brakes-on-its-explosive-growth/?slreturn=20230510140111
+
+% https://www.google.com/search?channel=fs&client=ubuntu&q=glasdoor+meta+lawyer+salary
 

### 2023-06-11 docs/research/LaTeX/research.tex
Add charts about user engagement

@@
 
-\subsection*{Fines analysis}
-
-%Explore the fines imposed on Meta Platforms by regulatory authorities due to
-%GDPR violations. Examine the magnitude of the fines, both in absolute terms and
-%in relation to the company's financial performance. Compare the fines to Meta
-%Platforms' revenue, profits, or other financial indicators to assess their
-%significance.
-
-% TODO: cite
+\subsection*{GDPR Fines}
 
@@
 \end{figure}
+
+\subsection*{Financials}
 
@@
 
+asd
+
 % Assess the impact of GDPR non-compliance on Meta Platforms' stock performance.
@@
 
-\subsection*{Advertiser Reactions}
+\subsection*{Advertising}
 
-% Study the response of advertisers to GDPR non-compliance by Meta Platforms.
-% Examine whether there has been a shift in advertiser behavior, such as reduced
-% advertising spend, contract cancellations, or demands for stricter data
-% protection measures. Analyze the financial implications of these reactions on
-% Meta Platforms' advertising revenue.
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1.00\textwidth]{family-revenue-per-person}
+    \caption{Family Revenue per Person (FRP) of Meta Platforms,
+    Inc.\cite{2023q1,2021q2Slides,2019q4Slides}}
+    \label{fig:family-revenue-per-person}
+\end{figure}
 
-% Average revenue per person Trends in Our Monetization by Facebook User
-% Geography page 46 - advertising
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1.00\textwidth]{advertising-revenue-by-user-geography}
+    \caption{Advertising Revenue by User Geography of Meta Platforms, Inc.(in
+    billions of \$)\cite{2023q1,2021q2Slides,2019q4Slides}}
+    \label{fig:advertising-revenue-by-user-geography}
+\end{figure}
+
+% Geography page 46 - advertising !!!
 
@@
 
-% Investigate whether GDPR non-compliance has had any impact on Meta Platforms'
-% user base and user engagement metrics. Analyze changes in user growth rates,
-% active user counts, or user activity patterns following GDPR-related
-% incidents. Assess the potential financial consequences of any decline in user
-% metrics.
+asd
 
-% Daily Active People Monthly Active People Daily Active Users (DAUs) facebook -
-% per region Monthly Active Users (MAUs) facebook - per region
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1.00\textwidth]{family-dap}
+    \caption{Family Daily Active People (FDAP) of Meta Platforms, Inc.(in
+    billions)\cite{2023q1,2021q2Slides,2019q4Slides}}
+    \label{fig:family-dap}
+\end{figure}
 
-% https://d18rn0p25nwr6d.cloudfront.net/CIK-0001326801/5fb5d0ea-c2c7-46f0-a26a-656df1673fac.pdf
-% page 14 revenue from europe page 42 41 37 and onwards
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1.00\textwidth]{family-map}
+    \caption{Family Monthly Active People (FMAP) of Meta Platforms, Inc.(in
+    billions)\cite{2023q1,2021q2Slides,2019q4Slides}}
+    \label{fig:family-map}
+\end{figure}
 
-\section{Discussion}
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1.00\textwidth]{facebook-dau}
+    \caption{Facebook Daily Active Users (FDAU) of Meta Platforms, Inc.(in
+    billions)\cite{2023q1,2021q2Slides,2019q4Slides}}
+    \label{fig:facebook-dau}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1.00\textwidth]{facebook-mau}
+    \caption{Facebook Monthly Active Users (FMAU) of Meta Platforms, Inc.(in
+    billions)\cite{2023q1,2021q2Slides,2019q4Slides}}
+    \label{fig:facebook-mau}
+\end{figure}
+
+\section*{Discussion}
 
@@
 
+\section*{Conclusion}
+
 \bibliographystyle{vancouver}

### 2023-06-11 docs/research/LaTeX/research.tex
Fix bugs with image placement and references

@@
 \usepackage{url}
+\def\UrlBreaks{\do\/\do-}
 \usepackage{cite}
+\usepackage{float}
 \usepackage[font=footnotesize,labelfont=bf]{caption}
@@
     \item Articles published in English
-    \item Articles published between 2018 and 2023
-    \item Articles that discuss GDPR
-    \item Articles that discuss Meta Platforms, Inc.
+    \item Articles published after 2010
+    \item Data about GDPR fines
+    \item Data about \textit{Meta Platforms, Inc.} financials
     \item Data between 2018 and 2023
@@
     \item Articles published in languages other than English
-    \item Articles published before 2018
-    \item Articles that do not discuss GDPR
-    \item Articles that do not discuss Meta Platforms, Inc.
-    \item Articles that discuss about ethics
+    \item Articles published before 2010
+    \item Data that is not about GDPR fines
+    \item Data that is not about \textit{Meta Platforms, Inc.} financials
     \item Data before 2018
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
@@
 
-asd
-
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
     \includegraphics[width=1.00\textwidth]{facebook-dau}
-    \caption{Facebook Daily Active Users (FDAU) of Meta Platforms, Inc.(in
-    billions)\cite{2023q1,2021q2Slides,2019q4Slides}}
+    \caption{Facebook Daily Active Users (FDAU) by Geographical Location of Meta
+    Platforms, Inc.(in billions)\cite{2023q1,2021q2Slides,2019q4Slides}}
     \label{fig:facebook-dau}
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
     \includegraphics[width=1.00\textwidth]{facebook-mau}
-    \caption{Facebook Monthly Active Users (FMAU) of Meta Platforms, Inc.(in
-    billions)\cite{2023q1,2021q2Slides,2019q4Slides}}
+    \caption{Facebook Monthly Active Users (FMAU) by Geographical Location of
+    Meta Platforms, Inc.(in billions)\cite{2023q1,2021q2Slides,2019q4Slides}}
     \label{fig:facebook-mau}

### 2023-06-11 docs/research/LaTeX/research.tex
Add stock price and volume performance
Add grafana chart setup

@@
 \textbf{Balance Sheets}, \textbf{Income Statements} and \textbf{Form 10-Q}.
+Stock performance data has been gathered from the official \textit{Yahoo!
+Finance} website\cite{stockPrice}.
 
@@
 
-This study is approved by Fontys University of Applied Sciences, Eindhoven, The
-Netherlands. All data is collected from publicly available sources and no
-personal data is collected. The author is not affiliated with Meta Platforms,
-Inc. or any other company mentioned in this study.
+This study is approved by \textit{Fontys University of Applied Sciences,
+Eindhoven, The Netherlands}. All data is collected from publicly available
+sources and no personal data is collected. The author is not affiliated with
+\textit{Meta Platforms, Inc.} or any other company mentioned in this study.
 
@@
 
-asd
-
 % Assess the impact of GDPR non-compliance on Meta Platforms' stock performance.
@@
 % investor confidence and the company's market capitalization.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=1.00\textwidth]{stock-price}
+    \caption{Stock Price Performance of Meta Platforms, Inc. (META) (in
+    \$)\cite{stockPrice}}
+    \label{fig:stock-price}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=1.00\textwidth]{volume}
+    \caption{Volume of Meta Platforms, Inc. (META) (in millions of
+    shares)\cite{stockPrice}}
+    \label{fig:volume}
+\end{figure}
 

### 2023-06-11 docs/research/LaTeX/research.tex
Fix references

@@
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=1.00\textwidth]{violations-by-article}
-    \caption{Number of violations by GDPR
-    article\cite{gdprFine1,gdprFine2,gdprFine3,gdprFine4,gdprFine5,gdprFine6,gdprFine7,gdprFine8,gdprFine9}}
-    \label{fig:violations-by-article}
-\end{figure}
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[width=1.00\textwidth]{violations-by-article}
+%     \caption{Number of violations by GDPR
+%     article\cite{gdprFine1,gdprFine2,gdprFine3,gdprFine4,gdprFine5,gdprFine6,gdprFine7,gdprFine8,gdprFine9}}
+%     \label{fig:violations-by-article}
+% \end{figure}
 
@@
 \subsection*{Investor Confidence and Stock Performance}
-
-% Assess the impact of GDPR non-compliance on Meta Platforms' stock performance.
-% Analyze stock price movements, market reactions to GDPR-related news, and
-% changes in investor sentiment. Explore how GDPR issues have influenced
-% investor confidence and the company's market capitalization.
 
@@
 \end{figure}
-
-% Geography page 46 - advertising !!!
 
@@
 \section*{Discussion}
+% Geography page 46 - advertising !!!
 
-% % Investigate the costs incurred by Meta Platforms in legal proceedings
-% related to GDPR non-compliance. This includes expenses associated with hiring
-% legal counsel, litigation, settlement agreements, and any ongoing legal
-% obligations. Analyze the financial impact of these legal expenses on the
-% company's profitability. Reputational Damage Assess the financial impact of
-% reputational damage resulting from GDPR non-compliance. Investigate whether
-% negative media coverage, public backlash, or loss of user trust have affected
-% Meta Platforms' brand value or customer perception. Analyze any associated
-% costs, such as brand recovery campaigns or decreased user acquisition rates.
+% state the results of each graph state what I want the readers to see from each
+% graph
 
-% hard to assess
+% connections
 
-% https://www.law.com/corpcounsel/2021/11/24/as-regulators-hover-meta-expands-legal-department/
-
-% https://www.law.com/corpcounsel/2022/11/10/meta-cuts-hit-legal-department-slamming-brakes-on-its-explosive-growth/?slreturn=20230510140111
-
-% https://www.google.com/search?channel=fs&client=ubuntu&q=glasdoor+meta+lawyer+salary
-
+The limitations of this study are that it does not consider the legal expenses
+incurred by \textit{Meta Platforms, Inc.} in relation to GDPR non-compliance.
+This includes expenses associated with hiring legal counsel, litigation,
+settlement agreements, and any ongoing legal obligations. It also does not
+consider the financial impact of reputational damage resulting from GDPR
+non-compliance. Moreover, it does not investigate whether negative media
+coverage, public backlash, or loss of user trust have affected \textit{Meta
+Platforms'} brand value or customer perception. Further research could be done
+into those areas.
 \section*{Conclusion}

### 2023-06-11 docs/research/LaTeX/research.tex
Add discussion and conclusion

@@
     \item Articles published after 2010
-    \item Data about GDPR fines
+    \item Data about GDPR fines above 1 million EUR
     \item Data about \textit{Meta Platforms, Inc.} financials
@@
     \item Articles published before 2010
-    \item Data that is not about GDPR fines
+    \item Data that is about GDPR fines below 1 million EUR
     \item Data that is not about \textit{Meta Platforms, Inc.} financials
@@
 
-% \begin{figure}[H]
-%     \centering
+% \begin{figure}[H] \centering
 %     \includegraphics[width=1.00\textwidth]{violations-by-article}
@@
 %     article\cite{gdprFine1,gdprFine2,gdprFine3,gdprFine4,gdprFine5,gdprFine6,gdprFine7,gdprFine8,gdprFine9}}
-%     \label{fig:violations-by-article}
-% \end{figure}
+%     \label{fig:violations-by-article} \end{figure}
 
@@
 
+Comparing net income and monetarial amount of GDPR fines shows little to no
+signs of correlation. Since the first GDPR fine was issued in 2021 as displayed
+in Figure \ref{fig:amount-of-gdpr-fines}, the net income has decreased by 46.7\%
+as displayed in Figure \ref{fig:net-income}. However, this can be attributed to
+other macroeconomic factors because the net income of other large technology
+companies such as \textit{Amazon.com, Inc.} and \textit{Alphabet, Inc.}, has
+also decreased in a similar fashion\cite{amznNetIncome,googleNetIncome}. Figure
+\ref{fig:rel-fines-net-income} below shows a comparison between both figures.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=1.00\textwidth]{rel-fines-net-income}
+    \caption{Comparison between Net Income and Monetarial Amount of GDPR Fines}
+    \label{fig:rel-fines-net-income}
+\end{figure}
+
+Similarly, the revenue is not affected as well. Figure
+\ref{fig:rel-fines-revenue} below shows a comparison between revenue and the
+monetarial amount of GDPR fines.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=1.00\textwidth]{rel-fines-revenue}
+    \caption{Comparison between Revenue and Monetarial Amount of GDPR Fines}
+    \label{fig:rel-fines-revenue}
+\end{figure}
+
+Figure \ref{fig:stock-price} shows that the first GDPR fine might have had a
+negative impact on the stock price, but subsequent more severe fines did not. In
+fact, the latest record-breaking fine of \$1.2 billion shows an opposite trend
+where the stock price continues to increase from \$234 to \$265 by the time this
+report was written. It is worth noting that the stock price reaction might
+experience a delay based on whether the fine will be imposed or not as
+\textit{Meta} is arguing against the fine \cite{metaArgueFine}.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=1.00\textwidth]{rel-fines-stock-price}
+    \caption{Comparison between Stock Price and Monetarial Amount of GDPR Fines}
+    \label{fig:rel-stock-price}
+\end{figure}
+
+Likewise, the unchanged volume of shares traded signals no decrease in investor
+confidence as displayed in Figure \ref{fig:volume}. Figure
+\ref{fig:rel-fines-volume} below shows a comparison between the volume of shares
+traded and the monetarial amount of GDPR fines.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=1.00\textwidth]{rel-fines-volume}
+    \caption{Comparison between Stock Volume and Monetarial Amount of GDPR Fines}
+    \label{fig:rel-fines-volume}
+\end{figure}
+
+The average revenue per person shows no signs of correlation with the monetarial
+amount of GDPR fines as shown in Figure \ref{fig:family-revenue-per-person}.
+
+Dividing the average revenue per person by user geography region shows that
+\textit{Meta's} revenue per person in Europe is less volatile than people in the
+US despite Europe having nearly twice the users compared to the United
+States\cite{2023q1}. The period from 31-Mar-2022 to 31-Dec-2022 is very
+different from the rest of the timeline because a \%6.45 increase in revenue in
+the US was met with a \%10.77 decline in revenue in Europe. Figure
+\ref{fig:rel-fines-avg-revenue-per-person-region} below shows a comparison
+between the average revenue per person by user geography region and the
+monetarial amount of GDPR fines.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=1.00\textwidth]{rel-fines-avg-revenue-per-person-region}
+    \caption{Comparison between Average Revenue per Person by User Geography Region and Monetarial Amount of GDPR Fines}
+    \label{fig:rel-fines-avg-revenue-per-person-region}
+\end{figure}
+
+Figure \ref{fig:facebook-mau} and Figure \ref{fig:facebook-dau} show that the
+number of daily and monthly active users in Europe has been steadily increasing
+regardless of the fines imposed. It is worth noting that this increase seems to
+be slowing down. Other regions show a similar trend with some showing a
+shrinkage in the number of users.
+
 The limitations of this study are that it does not consider the legal expenses
@@
 
+In summary, the fines imposed on \textit{Meta Platforms, Inc.} under the GDPR
+have not had a substantial impact on the company's financial performance.
+Investor confidence remains intact, as evidenced by the stability of the stock
+price and trading volume around the time of the fines. Furthermore, the
+company's revenue and net income have not been adversely affected by these
+penalties. The only noticeable change is the less volatile average revenue per
+person in Europe compared to the US. Especially in the period from 31-Mar-2022
+to 31-Dec-2022 where a \%6.45 increase in revenue in the US was met with a
+\%10.77 decline in revenue in Europe.
+
 \bibliographystyle{vancouver}

### 2023-06-11 docs/research/LaTeX/research.tex
Finish paper

@@
 \begin{abstract}
-    % TODO
+    This paper investigates the financial implications of General Data
+    Protection Regulation (GDPR) fines on \textit{Meta Platforms, Inc.}
+    (formerly \textit{Facebook, Inc.}). By examining net income, revenue, stock
+    price, volume of shares traded, and average revenue per person, the study
+    assesses the relationship between GDPR penalties and Meta's financial
+    performance. The findings suggest that GDPR fines did not have any impact,
+    with investor confidence remaining stable, revenue unaffected, and net
+    income declining in line with other tech companies. However, a slight
+    decline in average revenue per person in Europe compared to the US is
+    observed. Further research is needed to explore legal expenses, reputation,
+    and user perception related to GDPR non-compliance.
 \end{abstract}
@@
 
-In summary, the fines imposed on \textit{Meta Platforms, Inc.} under the GDPR
+In conclusion, the fines imposed on \textit{Meta Platforms, Inc.} under the GDPR
 have not had a substantial impact on the company's financial performance.
